\documentclass[11pt]{article}

\usepackage[a4paper,margin=24mm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,longtable,array}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage[dvipsnames,table]{xcolor}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{pdflscape}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,calc,fit}
\usepackage[hidelinks]{hyperref}

\setlength{\emergencystretch}{4em}
\setlist{nosep}
\renewcommand{\arraystretch}{1.18}

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{remark}[definition]{Remark}

\tikzset{
  ctauthor/.style={rectangle,draw=RoyalBlue!75!black,fill=RoyalBlue!8,
    rounded corners=1.5pt,align=left,text width=4.65cm,minimum height=1.55cm,
    inner sep=3pt,font=\scriptsize},
  ctpred/.style={rectangle,draw=BurntOrange!80!black,fill=BurntOrange!9,
    rounded corners=1.5pt,align=left,text width=4.65cm,minimum height=1.55cm,
    inner sep=3pt,font=\scriptsize},
  ctderived/.style={rectangle,draw=ForestGreen!70!black,fill=ForestGreen!8,
    rounded corners=1.5pt,align=left,text width=4.65cm,minimum height=1.55cm,
    inner sep=3pt,font=\scriptsize},
  ctnode/.style={rectangle,draw=black!75,fill=black!3,rounded corners=1.5pt,
    align=left,text width=5.10cm,minimum height=1.70cm,inner sep=3pt,font=\scriptsize},
  ctentry/.style={ctnode,draw=RoyalBlue!80!black,fill=RoyalBlue!10},
  ctdecision/.style={ctnode,draw=Purple!75!black,fill=Purple!8},
  ctloop/.style={ctnode,draw=BurntOrange!85!black,fill=BurntOrange!10},
  ctcertificate/.style={ctnode,draw=ForestGreen!80!black,fill=ForestGreen!12},
  ctresidual/.style={ctnode,draw=BrickRed!80!black,fill=BrickRed!9},
  ctroute/.style={rectangle,draw=Purple!80!black,fill=Purple!9,dashed,
    rounded corners=2pt,align=center,text width=6.3cm,minimum height=1.35cm,
    inner sep=3pt,font=\scriptsize},
  ctinputarrow/.style={-{Latex[length=1.6mm]},RoyalBlue!75!black,thin},
  ctpredarrow/.style={-{Latex[length=1.6mm]},BurntOrange!80!black,thin},
  ctderivedarrow/.style={-{Latex[length=1.6mm]},ForestGreen!75!black,thin},
  ctedge/.style={-{Latex[length=1.9mm]},black!70,thick},
  ctloopedge/.style={-{Latex[length=1.9mm]},BurntOrange!85!black,thick,dashed},
  ctroutearrow/.style={-{Latex[length=1.9mm]},Purple!80!black,thick,dashed},
  ctedgelabel/.style={font=\tiny,fill=white,inner sep=1pt,text=black!75}
}

\title{Structural Exhaustion as an Automation-First Lean Library\\
\large Exact sequential machines, minimal capability interfaces, and explicit residual routing}
\author{Framework reference generated from the Lean implementation}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
The structural-exhaustion library implements seventeen closure tactics as
exact sequential machines in Lean.  A problem instantiation supplies primitive
mathematical vocabulary, explicit finite enumerators, decision procedures, and
problem-specific primitive operators.  The library derives exhaustive searches,
predecessor-indexed states, certificates, residuals, graph paths, reference
execution, soundness, totality, and determinism.  Route modules derive typed
triggers, context preservation, and provenance from semantic residuals; a route
whose source does not canonically determine the consumer seed also receives a
problem-specific semantic adapter.  The compiled Lean environment is the
formal authority.  This document records the common contracts and includes a
generated description and diagram for every tactic.  Each diagram separates
problem-specific static inputs from inherited state and framework-derived data
at every node.  Four independent Lake packages exercise the public graph
interfaces: complete proofs of the even-cycle theorem, greedy coloring, and
Mantel's theorem, together with a partial formalization of the initial CT
reductions for Erd\H{o}s Problem~64.
\end{abstract}

\tableofcontents

\section{Formal authority and design objective}

The library has one formal source: the modules below
\texttt{lean/StructuralExhaustion}.  The JSON catalog, schemas, figures, and
tables are projections of compiled declarations.  A topology change begins in
an inductive \texttt{Graph.NodeId} or \texttt{Graph.Edge}; an interface change
begins in a \texttt{Spec}, \texttt{Capability}, or automation contract.

Worked theorem instantiations are separate consumers.
\texttt{examples/even\_cycle}, \texttt{examples/greedy\_coloring},
\texttt{examples/mantel}, and \texttt{examples/erdos\_64\_eg} are Lake
packages that import the framework through its public module names.  Their
code does not contribute to the compiled CT catalog.  The framework and all
four examples pin Lean and Mathlib 4.31.0.

The design objective is to minimize proof-instance code.  A problem instance
provides only data whose meaning depends on the concrete theorem.  Every
operation determined by finite search, verified computation, or a reusable
theorem belongs to the framework.  This boundary permits one node to be
formalized and audited against stable predecessor and successor types while
the remainder of the machine stays unchanged.

The reusable graph layer follows the same rule.  Its ambient graphs are
Mathlib \texttt{SimpleGraph} values.  It uses Mathlib's \texttt{Dart},
\texttt{Walk}, \texttt{Path}, \texttt{Walk.IsCycle},
\texttt{neighborFinset}, \texttt{degree}, \texttt{minDegree}, graph inclusion,
and \texttt{deleteEdges}.  The layer adds only ordered execution input,
dependent rooted-path state, cycle-length certificates, deterministic maximal
path execution, and one-edge deletion lemmas not supplied directly by
Mathlib.

The reusable minimum-degree/cycle boundary is
\texttt{Graph.MinimumDegreeCycle.StaticInput}.  For a branch-state family, a
natural-number degree threshold, and a decidable predicate on cycle lengths,
it generates the shared \texttt{Core.Problem}, the Mathlib cycle target and
its complete CT1 encoding, and the deletion-only CT2 capability and closure
rule.  Thus graph applications do not reimplement dart enumeration, cycle
coding, degree preservation, edge-count decrease, or cycle transport.

The reusable \texttt{Graph.EndpointParityCycle.Profile} builds on this
boundary.  From a minimum-degree/cycle profile, a proof that its threshold is
at least three, and an interpretation of even lengths, it generates the
greedy maximal path, the CT6 active-ledger run, the typed CT6-to-CT9 route, the
CT9 parity-overload run, localization of the two path positions, the Mathlib
chord cycle, the target theorem, and its exact CT1 validation run.  The
canonical \texttt{Profile.evenCycle} fixes all of these inputs for the worked
even-cycle theorem.

The reusable \texttt{Graph.GreedyColoring} layer provides a second graph
profile.  It computes the maximum degree, constructs a bounded elimination
order, executes CT12 on the corresponding head-peeling schedule, and performs
a reverse coloring fold.  Each fold step invokes the CT4
\texttt{FunctionalCardinalityProfile}: later-neighbour slots are payers and
the $\Delta+1$ colors are demands.  Functional eligibility and the strict
cardinality inequality force CT4 to return a missing color.  The resulting
Mathlib coloring is checked by the generated CT1 target encoding.

\input{generated/catalog-status.tex}

\subsection{Root problem and shared contexts}

\begin{definition}[Root problem]
A root problem consists of an ambient type $\mathcal A$, a baseline predicate
$B:\mathcal A\to\mathsf{Prop}$, a rank $\rho:\mathcal A\to\mathbb N$, and a
type of branch states.  In Lean these fields form \texttt{Core.Problem}.
\end{definition}

\begin{definition}[Branch context]
For a root problem $P$, a branch context contains an object $G:\mathcal A$, a
branch state, and a proof of $B(G)$.  Given a target predicate $T$, an avoiding
context adds $\neg T(G)$.  A minimal-counterexample context adds
\[
  \forall H,\quad \rho(H)<\rho(G)\longrightarrow B(H)\longrightarrow T(H).
\]
The ambient object and branch state occur once, as indices shared by all
tactics and routes.
\end{definition}

This indexing removes context reconstruction from tactic interfaces.  A route
may refine the logical context, for example by adding target avoidance and
minimality, while retaining the same ambient object and branch state by
definition.

\section{Mathlib foundation and exact finite computation}

The library is a Mathlib package.  Its finite types, finite sets, sums,
cardinalities, parity facts, and graph semantics use Mathlib declarations.
Framework-owned structures are retained only when they express observable
machine semantics that the underlying mathematical structure does not fix.

\begin{definition}[Explicit finite enumerator]
An explicit finite enumerator of a type $X$ is a Mathlib
\texttt{FinEnum X} value.  It contains a cardinal $n$, an equivalence
$X\simeq\operatorname{Fin}(n)$, and decidable equality.  Mathlib's
\texttt{FinEnum.toList} derives a duplicate-free exhaustive list.  CT
capabilities store the enumerator as a value, so two machines may declare
different deterministic orders on the same finite type without changing its
mathematical \texttt{Fintype} structure.
\end{definition}

An ordered partial collection is a duplicate-free list without an
exhaustiveness claim.  It is used only when first-hit order is observable, for
example in a finite-saturation frontier or a routed CT9 item collection.
Unordered finite subsets and all order-insensitive cardinality arguments use
Mathlib \texttt{Finset}.

\begin{proposition}[Reference search]
Let $p:X\to\mathsf{Prop}$ be decidable and let $E$ be an exact finite
enumerator of $X$.  The reference search returns either
\begin{enumerate}
  \item a value $x$ with a proof of $p(x)$, or
  \item a function assigning every $x:X$ a proof of $\neg p(x)$.
\end{enumerate}
The result is deterministic for the declared order.  The first-hit variant
also proves that no earlier element satisfies $p$.
\end{proposition}

Dependent search provides the analogous result for witness families
$W(x)$.  Exact observations package Boolean baseline and target evaluations
with reflection theorems.  Equality of exact observations therefore transports
both baseline truth and target avoidance.  A smaller-object constructor stores
the object and its rank decrease together, allowing the shared minimality
theorem to close every smaller counterexample uniformly.

\section{Provision-tagged API contracts}

Each declaration used by a node has a provenance in
\texttt{Core.Provision}.  The taxonomy is shown in
Table~\ref{tab:provision-taxonomy}.

\begin{table}[ht]
\centering
\small
\begin{tabular}{@{}ll@{}}
\toprule
Class & Meaning \\
\midrule
\texttt{framework\_constant} & fixed declaration supplied by the library \\
\texttt{user\_definition} & problem-specific type or predicate \\
\texttt{user\_operator} & problem-specific primitive operation \\
\texttt{user\_finite\_enumeration} & explicit Mathlib \texttt{FinEnum} fixing reference order \\
\texttt{typeclass\_inferred} & instance synthesized by Lean \\
\texttt{derived\_definitionally} & constructor or equality by reduction \\
\texttt{derived\_from\_predecessor} & value fixed by the incoming indexed state \\
\texttt{derived\_by\_generic\_search} & exhaustive framework search \\
\texttt{derived\_by\_generic\_theorem} & reusable framework theorem \\
\texttt{derived\_by\_computation} & verified deterministic calculation \\
\texttt{instance\_bridge} & explicit problem-specific decision, equality, or semantic bridge \\
\texttt{optimized\_implementation} & implementation proved equal to the reference \\
\texttt{policy\_selected} & deterministic registered selection policy \\
\texttt{generated\_route} & typed route object constructed by the framework \\
\texttt{generated\_audit} & graph, trace, or verification artifact \\
\bottomrule
\end{tabular}
\caption{Provision taxonomy exported by the compiled Lean catalog.}
\label{tab:provision-taxonomy}
\end{table}

For each executable node, \texttt{NodeAutomationContract} records the
execution class, problem-specific static inputs, inferred and predecessor inputs,
framework dependencies, theorems, generated outputs, and remaining manual
obligations.  All reference machines in this library have an empty list of
manual node obligations.  This count concerns tactic nodes; independently
declared cross-tactic semantic adapters are recorded by the route contract.
Terminal contracts are generated from their incoming edge constructors and the
trace theorem.

\section{Exact sequential tactic machines}

For a fixed tactic instance, \texttt{Graph.Edge} is indexed by its source and
target node identifiers.  An edge constructor carries the mathematical state
required by its successor.  The inductive path type is consequently
well-typed by construction:
\[
  \mathsf{Path}(a,c)
  \;::=\; \mathsf{nil}(a)
  \mid \mathsf{cons}\bigl(\mathsf{Edge}(a,b),\mathsf{Path}(b,c)\bigr).
\]
An execution result contains a terminal $t$, a path from the entry node to the
node represented by $t$, and an outcome indexed by $t$.

\paragraph{Public execution API.}
For every closure tactic, the public \texttt{run} function returns this
evidence-carrying \texttt{ExecutionResult}.  There is no outcome-only public
runner.  The notation \texttt{ctN\_execute} invokes \texttt{run};
\texttt{ctN} applies \texttt{run\_verified}; and \texttt{ctN\_total} applies
\texttt{run\_total}.  Thus invocation, semantic verification, and totality use
the same compiled reference execution.

Every tactic exposes the following standard theorem surface.
\begin{longtable}{@{}p{0.30\linewidth}p{0.64\linewidth}@{}}
\toprule
Declaration & Contract \\
\midrule
\endhead
\texttt{run} & returns the terminal, typed path, and terminal-indexed evidence in one result \\
\texttt{ctN\_execute} & term syntax for the corresponding public runner \\
\texttt{ctN} & tactic syntax for semantic soundness of that run \\
\texttt{ctN\_total} & tactic syntax for totality and typed-trace validity \\
\texttt{run\_verified} & the returned certificate or residual satisfies its semantic predicate \\
\texttt{run\_trace\_valid} & the recorded trace is represented by an indexed path \\
\texttt{run\_total} & reference execution returns verified evidence and a valid trace \\
\texttt{run\_deterministic} & two results equal to reference execution are equal \\
\texttt{outcome\_exhaustive} or \texttt{run\_exhaustive} & every result belongs to the declared terminal family \\
\bottomrule
\end{longtable}

Some nodes are explicit audit boundaries.  Their outgoing edges are tagged
\texttt{generated\_audit}; an edge may be nullary or may carry typed evidence,
as specified by its constructor.  The tag records the edge's role in the
machine rather than its payload cardinality.  The diagrams distinguish these
audit edges from states, decisions, certificates, and residuals.

Reference semantics follow the order of each explicit finite enumerator or
ordered partial collection.
An optimized implementation is admissible after proving equality with this
reference result.  The proof fixes both the semantic outcome and its
provenance.

\section{Semantic residuals and typed routes}

A tactic returns a closure certificate or a semantic residual.  A residual
contains the obstruction proved by the source tactic and inherits its branch
context as a dependent index.  Consumer selection belongs to the route layer.

\begin{definition}[Route rule]
For a residual type $R$ and a target tactic interface $J$, a route rule
contains a stable identifier, a target-context function, a residual-indexed
seed type, constructive seed discovery, and a trigger constructor
\[
  \mathsf{buildTrigger}:
  \prod_{r:R}\mathsf{Seed}(r)\to
  J.\mathsf{Trigger}(\mathsf{targetContext}(r)).
\]
\end{definition}

Enabled discovery supplies a seed and therefore a well-typed trigger.
Disabled discovery supplies a proof that the seed type is empty.  Route
modules construct the trigger and prove context preservation, soundness, and
stable provenance once.  The route contract separately records its
semantic-discovery mode:
\begin{itemize}
  \item \texttt{capabilityDiscovery} uses discovery already supplied by the
  target capability and requires no residual-specific adapter;
  \item \texttt{problemSemanticAdapter} requires one reusable interpretation
  of the source residual as consumer seed data.
\end{itemize}
The CT1-avoidance-to-CT2 route uses CT2 capability discovery together with the
shared \texttt{MinimalityKernel} that upgrades the avoiding context to a
minimal-counterexample context; it needs no residual-specific adapter.  The
CT2-separating-context-to-CT3 route receives a \texttt{PieceDiscovery}
adapter, and the CT2-criticality-to-CT10 route receives a
\texttt{DataDiscovery} adapter.  These adapters expose only residual-specific
seed discovery and extraction.  Framework declarations construct the
destination trigger, preserve the inherited context, and prove route soundness
and provenance.

The CT6-active-ledger-to-CT9 route receives an
\texttt{ItemCollectionAdapter}.  Its sole field maps the typed active-ledger
residual to CT9's duplicate-free finite item collection.  The route is then
forced: the framework constructs the trigger and runner input, preserves the
branch context and CT6 activity evidence, and records provenance.

\begin{table}[ht]
\centering
\small
\begin{tabular}{@{}p{0.29\linewidth}p{0.65\linewidth}@{}}
\toprule
Route & Authoring boundary \\
\midrule
\texttt{CT1.residual.avoiding}\newline
$\to$ \texttt{CT2} &
Mode: \texttt{capabilityDiscovery}.\newline
Inputs: \texttt{targetCapability}, \texttt{minimalityKernel}.\newline
Adapter: $\varnothing$. \\
\addlinespace
\texttt{CT2.residual.}\newline
\texttt{separatingContext}\newline
$\to$ \texttt{CT3} &
Mode: \texttt{problemSemanticAdapter}.\newline
Inputs: \texttt{targetCapability}, \texttt{semanticDiscoveryAdapter}.\newline
Adapter: \texttt{PieceDiscovery}. \\
\addlinespace
\texttt{CT2.residual.criticality}\newline
$\to$ \texttt{CT10} &
Mode: \texttt{problemSemanticAdapter}.\newline
Inputs: \texttt{targetCapability}, \texttt{semanticDiscoveryAdapter}.\newline
Adapter: \texttt{DataDiscovery}. \\
\addlinespace
\texttt{CT6.residual.activeLedger}\newline
$\to$ \texttt{CT9} &
Mode: \texttt{problemSemanticAdapter}.\newline
Inputs: \texttt{targetCapability}, \texttt{semanticDiscoveryAdapter}.\newline
Adapter: \texttt{ItemCollectionAdapter}. \\
\bottomrule
\end{tabular}
\caption{Problem-specific route inputs in the compiled registry.}
\label{tab:route-authoring-boundary}
\end{table}

For all four routes, the framework owns route-rule and target-context
construction, trigger construction, soundness, context preservation, and
provenance.  The \texttt{capabilityDiscovery} mode removes only the
residual-specific adapter; the target capability and any listed context theorem
remain problem inputs.

\section{CT1 and CT2 reference semantics}

\subsection{CT1: finite target realization}

For a branch object $G$, CT1 receives a finite test-index type $I$, a witness
family $W(G,i)$, and a predicate $\mathsf{Realizes}(G,i,w)$.  The target is
defined by
\[
  T(G)\;:\!\!\iff\;\exists i:I,\ \exists w:W(G,i),\
  \mathsf{Realizes}(G,i,w).
\]
The target-equivalence node is therefore definitional.  Dependent finite
search returns a realization and a C1 certificate, or proves the absence of
every realization.  The latter proof constructs the target-avoiding residual
and the shared avoiding context.  Route discovery begins only after this
semantic result has been established.

The proof-specific CT1 interface contains the test type, witness family,
realization predicate, explicit enumerators, and realization decider.  Search,
equivalence, certificate construction, avoidance, paths, and routing are
framework operations.  The equivalence is definitional for the canonical
\texttt{CT1.Target}.  A theorem stated with an independently named public
target may supply the optional \texttt{TargetBridge}; this one semantic bridge
relates the public predicate to the canonical target and is not a node or route
obligation.

\subsection{CT2: minimal deletion and exhaustive replacement}

CT2 operates in a shared minimal-counterexample context.  Its primitive
systems provide finitely enumerated pieces, a piece-to-interface map, compatible contexts,
baseline and target decision procedures, deletion, and exact legal
replacements with rank decrease.  The interface type itself need not be finite.
Explicit enumerators are required for the pieces of each ambient object, the
compatible contexts of the selected interface, and the legal candidates for
the selected piece.

Before core execution, \texttt{Capability.discover} (or
\texttt{ct2\_discover}) exhaustively selects the first proper admissible piece
in the declared \texttt{FinEnum} order.  Enabled discovery constructs the
proof-carrying \texttt{CT2.Input}; disabled discovery contains a proof that no
CT2 seed exists.  The public \texttt{run} function consumes the enabled input
and does not repeat this search.  Discovery is therefore a route-facing
pre-step rather than a \texttt{CT2.Graph.NodeId}.  The selected seed and the
minimal-counterexample context form the complete CT2 invocation.

Deletion first produces either a smaller counterexample or a proof that the
deleted object is not a counterexample.  In the former case the shared
minimality theorem yields C2.  In the latter case CT2 searches all legal
replacement candidates.  A candidate is equivalent precisely when its exact
baseline/target observation agrees with the source observation in every
compatible context.  An equivalent smaller counterexample again yields C2.

If no equivalent candidate exists, exhaustive comparison constructs a table
that assigns every candidate a concrete separating context.  A nonempty
candidate universe yields a separating-context residual and the complete
table.  An empty universe yields the criticality residual.  These residuals
feed the CT3 and CT10 route rules, respectively.

\section{Machine semantics for CT3--CT17}

Table~\ref{tab:automation-targets} summarizes the formal boundary used by the
remaining tactics.  The generated sections in
Section~\ref{sec:compiled-machines} give the exact Lean references.

\begin{longtable}{@{}p{0.07\linewidth}p{0.47\linewidth}p{0.40\linewidth}@{}}
\caption{Framework automation and problem-specific primitives.}
\label{tab:automation-targets}\\
\toprule
CT & Framework computation & Problem-specific primitives \\
\midrule
\endfirsthead
\toprule
CT & Framework computation & Problem-specific primitives \\
\midrule
\endhead
CT3 & exact-vector computation, compression search, table validation, then exact-row lookup & pieces, contexts, candidates, rows, exact responses, explicit finite enumerators, and primitive deciders \\
CT4 & one canonical assignment state, availability scan, fibre computation, overload search, then capacity comparison & demands, payers, eligibility, weights, capacities, explicit finite enumerators, decider, and required bound \\
CT5 & deficit search, deficit-free state, separate ledger summation, then fixed-priority arithmetic comparison & sites, dependent witnesses, active/support predicates, contributions, deciders, required amount, and capacity \\
CT6 & one ordered first-failure search or exhaustive active-ledger construction & indices, failure data and predicate, failure-data extractor, contributions, exact order, and failure decider \\
CT7 & realization search followed, only after exhaustive absence, by distinction search or neutrality & object pair, contexts, realization semantics, response function, explicit finite enumerator, and decider \\
CT8 & ordered repeated-type search followed by exact response comparison & state sequence, exact-type and response-context enumerators, response operator, and smaller-object removal \\
CT9 & nullary partition audit followed by on-demand exact-fibre overload search & finite item collection, labels, label map, and capacities \\
CT10 & nullary table audit, direct search, first class with an empty row, and terminal promotion audit & data, classes, class map, direct predicate, and promotion operator \\
CT11 & nullary decomposition audit, admissibility scan, then negative-budget localization & finite cell collection with negative-total proof, admissibility, and local budget \\
CT12 & current-cursor saturation, peeling, first restoration selection, and decrease-verified loop back & indexed states, peel operator, nonempty restoration options, and strict continuation decrease \\
CT13 & tier-one search, explicit absence state, canonical minimum-cost fallback, reconciliation, then demand comparison & payer/obstruction/resource universes, eligibility, costs, tier-two data, charge, and demand \\
CT14 & lower mass, complete member scan retaining that lower state, upper/multiplicity ledger, then comparison & members, lower mass, optional capacity and labels, and label equality \\
CT15 & input-indexed target-relative rank, first rank drop, full-rank ledger, then capacity comparison & coordinates, target dependence, primitive decider, charges, and capacity \\
CT16 & support exhaustion, closed-code computation, then literal equality split & coordinates, support predicate/decider, closed-code representation, and target code \\
CT17 & compatibility search, scale split, then finite survivor enumeration or orbit arithmetic & targets, offsets, scale-indexed positions, values, compatibility, finite scale bound, and equality deciders \\
\bottomrule
\end{longtable}

\section{Compiled CT1--CT17 machines}
\label{sec:compiled-machines}

The following sections are generated from
\texttt{StructuralExhaustion.Canonical.tactics}.  Each capability table is the
complete problem-specific surface.  The required-instance index refers only to
decision procedures and semantic bridges already listed in that table.  Each
node table gives the execution class, static inputs, predecessor and inferred
inputs, framework dependencies, and generated outputs.  All omitted
manual-obligation lists are empty.  The diagrams render the same node contracts,
and their graph arrows are compiled constructors of the indexed edge type.
Residual and route summaries are compact projections.  Each route summary
states whether residual-specific semantic-adapter authoring is required; the
generated JSON catalog retains the complete field-level contracts.

\input{generated/ct/CT1.tex}
\input{generated/ct/CT2.tex}
\input{generated/ct/CT3.tex}
\input{generated/ct/CT4.tex}
\input{generated/ct/CT5.tex}
\input{generated/ct/CT6.tex}
\input{generated/ct/CT7.tex}
\input{generated/ct/CT8.tex}
\input{generated/ct/CT9.tex}
\input{generated/ct/CT10.tex}
\input{generated/ct/CT11.tex}
\input{generated/ct/CT12.tex}
\input{generated/ct/CT13.tex}
\input{generated/ct/CT14.tex}
\input{generated/ct/CT15.tex}
\input{generated/ct/CT16.tex}
\input{generated/ct/CT17.tex}

\section{Instantiation and verification workflow}

A new theorem instantiation proceeds in four stages.
\begin{enumerate}
  \item Define one root problem and its initial branch context.
  \item Implement the primitive fields listed by the capabilities of the
  tactics used by the argument.  Explicit \texttt{FinEnum} values fix each
  exhaustive reference order; ordered partial collections fix any observable
  frontier order.
  \item Invoke the reference runners or tactic syntax.  The standard theorem
  surface supplies semantic soundness, totality, deterministic execution, and
  trace validity.
  \item For a route marked \texttt{problemSemanticAdapter}, implement its
  residual-to-seed discovery record.  The framework route receives that record,
  constructs the context-indexed target trigger, and supplies the routing
  theorems.  Routes marked \texttt{capabilityDiscovery} need no additional
  residual interpretation.
\end{enumerate}

Repository verification compiles all tactics and outcome fixtures, exports the
catalog from the compiled environment, validates graph and automation
invariants, rejects capability fields that inject completed results and rejects
admissions, regenerates every schema and figure, and compiles generated
declaration bindings.  The separate \texttt{make manuscript} target performs
those generation steps and then builds this document.  Together these checks
cover both the mathematical evidence flow and the advertised proof-instance
boundary.

\appendix

\section{External worked instantiation: an even cycle}
\label{app:even-cycle-example}

This appendix gives a complete finite-graph instantiation that is independent
of the Erd\H{o}s--Gy\'arf\'as application.  It proves the following theorem.

\begin{theorem}
Every finite simple graph of minimum degree at least three contains a simple
cycle of even length.
\end{theorem}

The positive minimum-degree hypothesis implies that the vertex type is
nonempty, so no separate nonemptiness field occurs in the formal statement.

\subsection{Package boundary}

The implementation is a separate Lake package rooted at
\texttt{examples/even\_cycle}.  Its \texttt{lakefile.toml} declares the
framework package in \texttt{lean/} as a path dependency.  The dependency is
one-way:
\[
  \texttt{EvenCycleExample}
  \longrightarrow
  \texttt{StructuralExhaustion}.
\]
No module below \texttt{lean/StructuralExhaustion} imports the worked example.
Thus the example exercises the same public interface available to a separate
repository.

\begin{table}[ht]
\centering
\small
\begin{tabular}{@{}p{0.31\linewidth}p{0.61\linewidth}@{}}
\toprule
Package & Authored content \\
\midrule
\texttt{lean/StructuralExhaustion} & Mathlib-backed finite enumeration and
search; CT1--CT17 capabilities and runners; typed paths, terminal evidence,
soundness, totality, determinism, finite saturation, residual theorems, and
routes; reusable \texttt{SimpleGraph} support for scheduled finite input,
rooted paths, cycle-length certificates, maximal paths, chord cycles, and
single-dart deletion; generated minimum-degree/cycle and endpoint-parity
profiles. \\
\texttt{examples/even\_cycle} & Selection of the canonical endpoint-parity
profile, thin theorem-facing aliases, and the executable K4 fixture.  It
introduces no graph, edge, walk, path, cycle, degree, deletion, CT6, or CT9
implementation. \\
\bottomrule
\end{tabular}
\caption{Physical separation between reusable framework code and the theorem
instance.}
\label{tab:even-cycle-package-boundary}
\end{table}

The framework contains a domain-independent CT layer and a reusable graph
support layer.  The former provides direct \texttt{FinEnum} combinators,
ordered finite saturation, canonical list-position and parity lemmas,
deletion-only CT2 closure, CT6 and CT9 exact-run bundles, and the
parity-capacity-one CT9 profile.  The graph layer supplies the common
minimum-degree/cycle profile, Mathlib cycle-code enumeration, and Mathlib
single-dart deletion.  Its endpoint-parity profile generates the reusable
maximal-path--CT6--CT9 argument.  It contains no
Erd\H{o}s--Gy\'arf\'as-specific predicate.

\subsection{Problem-specific objects}

For a vertex type $V$, the example consumes
\texttt{Graph.FiniteObject V}: a Mathlib \texttt{SimpleGraph V} together with
\texttt{Graph.FiniteInput G}.  The latter consists of an explicit
\texttt{FinEnum V} and \texttt{DecidableRel G.Adj}.  These values support the
Mathlib \texttt{Fintype}, \texttt{neighborFinset}, \texttt{degree},
\texttt{minDegree}, and \texttt{edgeFinset} APIs while fixing deterministic
machine order.  The graph profile generates the baseline
$3\leq G.\texttt{minDegree}$ and the target consisting of a Mathlib closed
walk satisfying \texttt{Walk.IsCycle} and having even length.

The framework's \texttt{RootedPath} is a dependent wrapper around Mathlib
\texttt{SimpleGraph.Path}; it records the active endpoint while keeping the
root fixed.  \texttt{Graph.GreedyPath.machine} uses the declared vertex order,
fresh-neighbour extension, and measure $|V|-|P|$.  Its terminal proof is
endpoint maximality.  A reusable chord theorem converts two distinct
same-parity endpoint-neighbour positions into a Mathlib
\texttt{Walk.IsCycle} certificate.

The external package therefore contains only a profile selection and public
names.  \texttt{Problem.lean} selects
\texttt{Graph.EndpointParityCycle.Profile.evenCycle}; its embedded
\texttt{MinimumDegreeCycle.StaticInput} is the single source for the problem,
target, CT1, and CT2.  \texttt{CT1Instance.lean},
\texttt{CT6Instance.lean}, \texttt{CT9Instance.lean}, and
\texttt{CT6CT9.lean} are thin aliases for generated framework declarations.
\texttt{Run.lean} exposes the generated theorem and CT1 run;
\texttt{Concrete.lean} fixes the K4 execution.  \texttt{CT2Audit.lean}
specializes the generated criticality theorem without adding a
graph-specific deletion proof.

\subsection{Exact tactic contracts}

Table~\ref{tab:even-cycle-static-contracts} lists every static input supplied
by the external package.  All searches, cardinality comparisons, residuals,
paths through tactic graphs, and terminal proofs are framework outputs.

\begin{longtable}{@{}p{0.13\linewidth}p{0.43\linewidth}p{0.36\linewidth}@{}}
\caption{Static contracts of the worked instantiation.}
\label{tab:even-cycle-static-contracts}\\
\toprule
Node & Problem-specific static inputs & Inherited invocation data \\
\midrule
\endfirsthead
\toprule
Node & Problem-specific static inputs & Inherited invocation data \\
\midrule
\endhead
Canonical profile & Selection of
\texttt{EndpointParityCycle.\allowbreak{}Profile.\allowbreak{}evenCycle V}.
This fixes
\texttt{PathState}, threshold $3$, even \texttt{LengthOK}, its decider, the
threshold proof, and the even-length interpretation. & Vertex type $V$ and
the ambient \texttt{FiniteObject V}. \\
Finite saturation & No additional problem-specific input.  The graph profile
generates \texttt{RootedPath}, the ordered vertex frontier,
\texttt{CanExtend}, prepend, the measure $|V|-|P|$, and its decrease proof. &
The ambient object and its baseline proof. \\
CT6 first-failure & No additional problem-specific input.  The endpoint-parity
profile generates the spec, capability, endpoint-maximality proof, exact run,
and endpoint-closure theorem. & Generated branch context containing $G$ and
the maximal path $P$. \\
CT6$\to$CT9 route & No additional problem-specific input.  The profile
generates the constant ordered-neighbour adapter and invokes the registered
typed route. & The generated CT6 active-ledger residual. \\
CT9 parity overload & No additional problem-specific input.  The profile
generates the path-position rank, parity-capacity-one capability, cardinality
bound, and exact overload run. & Routed branch context and ordered endpoint
neighbours. \\
Pair localization & No additional problem-specific input.  The profile
combines CT6 endpoint closure, Mathlib adjacency, and generic list-position
lemmas. & CT9's typed \texttt{SameParityPair} and the inherited path. \\
Cycle construction & No additional problem-specific input.  The profile
orients the positions and invokes the reusable Mathlib chord-cycle theorem. &
Localized positions and their adjacency, distinctness, and parity proofs. \\
Generated CT1 & No additional static input.  The common graph profile derives
bounded walk-support codes, their \texttt{FinEnum}, the cycle checker, the
specification, capability, and public-target bridge. & Original branch
context and the public even-cycle certificate. \\
Generated CT2 & No additional static input.  The common graph profile derives
Mathlib-dart enumeration, the endpoint-slack predicate, single-dart deletion,
rank decrease, baseline preservation, target transport, and the deletion-only
capability. & Minimal-counterexample context and an actual Mathlib dart. \\
\bottomrule
\end{longtable}

Figure~\ref{fig:even-cycle-machine-flow} shows the main pipeline.  Every
problem-specific static contract has an explicit edge to its consumer.  The
active-ledger residual is used both by the registered route and by pair
localization through endpoint closure.  The framework owns the
\texttt{FinEnum} combinators, exhaustive decision, finite saturation, CT1
target-encoding generation and public-target run, the CT6 active-ledger
bundle, the CT9 parity-capacity-one bundle, canonical list-position and parity
lemmas, the CT6-to-CT9 route, and deletion-only CT2 closure.  The external
package retains only the selection of the canonical endpoint-parity profile.
All CT6/CT9 semantic choices and their composition are framework declarations.

\begin{figure}[!ht]
\centering
\begin{tikzpicture}[node distance=4mm and 8mm]
  \node[ctauthor] (satin) {\textbf{Canonical profile selection}\\
    \texttt{Profile.evenCycle V}};
  \node[ctnode,right=of satin] (sat) {\textbf{Finite saturation}\\
    first-enabled execution; terminal path; no enabled terminal vertex};

  \node[ctderived,below=of satin] (ct6in) {\textbf{Generated CT6 API}\\
    vertex order; failure; contribution; decider; no-failure theorem};
  \node[ctdecision,right=of ct6in] (ct6) {\textbf{CT6 active-ledger run}\\
    exact execution, active residual, terminal, and trace};

  \node[ctderived,below=of ct6in] (routein) {\textbf{Generated route input}\\
    CT9 capability; constant neighbour-collection adapter};
  \node[ctdecision,right=of routein] (route) {\textbf{CT6$\to$CT9 buildInput}\\
    preserved branch context; declared CT9 item collection};

  \node[ctderived,below=of routein] (ct9in) {\textbf{Generated CT9 API}\\
    item type $V$; position rank; $3\le |N(v)|$};
  \node[ctdecision,right=of ct9in] (ct9) {\textbf{Parity-capacity-one run}\\
    generated Boolean labels; overload residual; same-parity pair};

  \node[ctderived,below=of ct9in] (pairin) {\textbf{Generated localization}\\
    neighbour interpretation; endpoint closure; path lookup};
  \node[ctnode,right=of pairin] (pair) {\textbf{Pair localization}\\
    distinct same-parity endpoint-neighbour positions};

  \node[ctderived,below=of pairin] (cyclein) {\textbf{Graph-layer theorem}\\
    Mathlib chord-cycle construction from two path positions};
  \node[ctcertificate,right=of cyclein] (cycle) {\textbf{Cycle construction}\\
    explicit simple even cycle; public \texttt{HasEvenCycle}};

  \node[ctderived,below=of cyclein] (ct1in) {\textbf{Generated CT1 profile}\\
    bounded walk-support codes; \texttt{FinEnum}; checker;
    encode/decode; spec/capability/bridge};
  \node[ctcertificate,right=of ct1in] (ct1) {\textbf{CT1 validation}\\
    generated spec/capability/bridge; exact C1 run};

  \draw[ctinputarrow] (satin) -- (sat);
  \draw[ctedge] (sat) -- (ct6);
  \draw[ctderivedarrow] (ct6in) -- (ct6);
  \draw[ctroutearrow] (ct6) -- (route);
  \draw[ctderivedarrow] (routein) -- (route);
  \draw[ctroutearrow] (route) -- (ct9);
  \draw[ctderivedarrow] (ct9in) -- (ct9);
  \draw[ctedge] (ct9) -- (pair);
  \draw[ctedge] (ct6.east) to[bend left=18]
    node[ctedgelabel,right]{endpoint closure} (pair.east);
  \draw[ctderivedarrow] (pairin) -- (pair);
  \draw[ctedge] (pair) -- (cycle);
  \draw[ctderivedarrow] (cyclein) -- (cycle);
  \draw[ctedge] (cycle) -- (ct1);
  \draw[ctderivedarrow] (ct1in) -- (ct1);
\end{tikzpicture}
\caption{Main sequential flow and node-local static inputs.  The public
even-cycle theorem is established at cycle construction; CT1 subsequently
validates the certificate through its exact reference machine.}
\label{fig:even-cycle-machine-flow}
\end{figure}

\subsection{Proof realized by the machines}

Let $P$ be the computed endpoint-maximal path and let $v$ be its active
endpoint.  CT6 searches the declared vertex \texttt{FinEnum} for a vertex adjacent to
$v$ and absent from $P$.  The terminal certificate of finite saturation
eliminates the first-failure outcome.  The resulting
\texttt{ActiveLedgerRun} contains the actual CT6 execution, its residual,
terminal, and trace.  Interpreting the residual's \texttt{noFailure} field
gives
\[
  N(v)\subseteq V(P).
\]
This is the only endpoint-closure fact used downstream.

The endpoint-parity profile instantiates CT6's vertex type, failure semantics,
capability, and endpoint-maximality proof.  The registered CT6-to-CT9 route
receives a framework-generated constant adapter returning the duplicate-free
collection $N(v)$.  The collection is determined by the inherited path; the
route still consumes the active-ledger residual and preserves its branch
context.  The graph profile supplies the item type and the rank
$x\mapsto\operatorname{idx}_P(x)$.  The CT9 profile generates
the Boolean label enumeration, parity labeling, and capacity one.  Since
$|N(v)|\ge3$ and total capacity is two,
\texttt{runParityCapacityOneOfThreeLeCardinality} returns the exact overloaded
run.  Its \texttt{pair} accessor yields distinct neighbours $x,y$ with equal
position parity.

The generic \texttt{locateDistinctPair} packages both canonical positions,
their bounds and lookup equations, and position distinctness.
The reusable graph-profile localization proof shows that both positions are endpoint
neighbours.  The subpath between them, together with the two endpoint chords
through $v$, is a simple cycle.  Its length is
\[
  |\operatorname{idx}_P(x)-\operatorname{idx}_P(y)|+2,
\]
which is even and at least four.  The reusable
\texttt{RootedPath.\allowbreak{}evenCycleOfEndpoint\allowbreak{}NeighborPositions}
theorem constructs
the Mathlib walk and proves \texttt{Walk.IsCycle} and the required length
predicate.  The endpoint-parity profile chooses the orientation and invokes
this theorem.

This record proves the public theorem
\texttt{EvenCycleExample.\allowbreak{}minimumDegreeThree\_\allowbreak{}hasEven\allowbreak{}Cycle}.
CT1 subsequently
validates the certificate.  The same
graph profile generates bounded Mathlib-walk support
codes, their direct \texttt{FinEnum}, the acceptance decider, semantic
encode/decode maps, the CT1 specification and capability, and the
\texttt{TargetBridge}.  The endpoint-parity profile's \texttt{ct1Run} invokes
\texttt{runC1OfPublicTarget} and packages the exact C1 execution and trace.

\subsection{Framework-generated CT2 deletion audit}

The deletion audit is independent of the CT6--CT9 proof.  It checks the common
minimum-degree/cycle API that is also used by the Erd\H{o}s~64 package.  Its
underlying minimum-degree/cycle contract has the following three static
components, all fixed by \texttt{Profile.evenCycle} in this application:
\begin{enumerate}
  \item the branch-state family \texttt{PathState};
  \item the minimum-degree threshold $3$;
  \item the predicate $\mathsf{LengthOK}(n)\iff n\bmod2=0$ together with its
  decision procedure.
\end{enumerate}
The vertex type and ambient finite graph are indices of an invocation rather
than additional fields of this record.

From these inputs, \texttt{Graph.MinimumDegreeCycle.StaticInput} generates the
root problem, its baseline and target, the complete CT1 encoding, and the
deletion-only CT2 capability.  CT2 pieces are Mathlib
\texttt{SimpleGraph.Dart} values, exhaustively ordered by the ambient
\texttt{FiniteInput}.  A dart is proper when both endpoint degrees are at
least $4$, and every dart is admissible.  The reduction uses Mathlib edge
deletion and the Mathlib edge-cardinality rank.  The graph layer proves strict
rank decrease, preservation of minimum degree, and transport of an accepted
Mathlib cycle along graph inclusion.

The generated \texttt{DeletionClosureRule} rules out a proper dart in a
minimal counterexample.  Combining this conclusion with the baseline gives
\[
  xy\in E(G)\quad\Longrightarrow\quad d(x)=3\ \text{or}\ d(y)=3.
\]
This is \texttt{StaticInput.dart\_has\_tight\_endpoint}; the example module
only exposes its specialization under theorem-specific names.
Figure~\ref{fig:even-cycle-ct2-flow} records the complete authoring boundary.

\begin{figure}[!ht]
\centering
\resizebox{0.99\linewidth}{!}{%
\begin{tikzpicture}[node distance=4mm and 8mm]
  \node[ctauthor] (statein) {\textbf{Static input 1}\\
    branch-state family \texttt{PathState}};
  \node[ctauthor,below=of statein] (degreein) {\textbf{Static input 2}\\
    minimum-degree threshold $3$};
  \node[ctauthor,below=of degreein] (lengthin) {\textbf{Static input 3}\\
    decidable $\mathsf{LengthOK}(n)\iff n\bmod2=0$};

  \node[ctderived,right=of degreein] (profile) {\textbf{Generated graph profile}\\
    problem; baseline; edge-count rank; Mathlib cycle target};
  \node[ctderived,above right=4mm and 8mm of profile] (ct1) {
    \textbf{Generated CT1}\\
    cycle codes; \texttt{FinEnum}; checker; bridge; capability};
  \node[ctderived,below right=4mm and 8mm of profile] (ct2) {
    \textbf{Generated CT2}\\
    darts; endpoint slack; deletion; closure rule; capability};

  \node[ctpred,below=of lengthin] (minimalin) {\textbf{Inherited invocation}\\
    minimal-counterexample context and an actual Mathlib dart};
  \node[ctcertificate,right=of minimalin] (tight) {
    \textbf{Tight-endpoint theorem}\\
    $d(x)=3$ or $d(y)=3$ for every dart $xy$};

  \draw[ctinputarrow] (statein.east) -- (profile.west);
  \draw[ctinputarrow] (degreein) -- (profile);
  \draw[ctinputarrow] (lengthin.east) -- (profile.west);
  \draw[ctderivedarrow] (profile) -- (ct1);
  \draw[ctderivedarrow] (profile) -- (ct2);
  \draw[ctpredarrow] (minimalin) -- (tight);
  \draw[ctedge] (ct2) -- (tight);
\end{tikzpicture}
}
\caption{Minimum-degree/cycle profile and its generated CT1/CT2 interfaces.
The three blue nodes are the static contract underlying the canonical profile
selection; Mathlib and the framework supply every operation shown in green.}
\label{fig:even-cycle-ct2-flow}
\end{figure}

\subsection{Closed execution fixture}

The K4 fixture fixes the vertex order and checks all reference choices by
computation.  It obtains the saturated path
$[v_3,v_2,v_1,v_0]$, endpoint-neighbour list $[v_0,v_1,v_2]$, and the explicit
four-cycle whose Mathlib walk support is
$[v_3,v_2,v_1,v_0,v_3]$.

\begin{table}[ht]
\centering
\small
\begin{tabular}{@{}lll@{}}
\toprule
Machine & Terminal & Erased trace \\
\midrule
CT6 & active ledger & entry, first-failure search, active-ledger terminal \\
CT9 & overload & entry, partition, overload, overloaded terminal \\
CT1 & C1 & entry, equivalence certification, realization decision, C1 terminal \\
\bottomrule
\end{tabular}
\caption{Kernel-checked terminals and traces for the K4 fixture.}
\label{tab:even-cycle-k4-traces}
\end{table}

\section{External partial instantiation: Erd\H{o}s Problem 64}
\label{app:erdos-64-example}

The independent package \texttt{examples/erdos\_64\_eg} fixes its public
statement to the right-hand side of \texttt{Erdos64.erdos\_64} in Google
DeepMind's \texttt{formal-conjectures} repository at commit
\texttt{bcaee6031a085e19432540650e1039b7fd1cea36}.  In Mathlib notation the
proposition is exactly
\begin{align*}
  \forall &(V:\mathsf{Type}^{*})\ (G:\mathsf{SimpleGraph}\ V)\
      [\mathsf{Fintype}\ V]\ [\mathsf{DecidableRel}\ G.\mathsf{Adj}],\\
  &G.\mathsf{minDegree}\ge 3 \ \longrightarrow\
    \exists (k:\mathbb N)\,(v:V)\,(c:G.\mathsf{Walk}\ v\ v),\\
  &\hspace{42mm} k\ge2\ \wedge\ c.\mathsf{IsCycle}\ \wedge\
    c.\mathsf{length}=2^k.
\end{align*}
The declaration \texttt{Erdos64EG.OfficialStatement} retains these
quantifiers, typeclass assumptions, and conclusion in Mathlib vocabulary.

For deterministic CT execution, the internal ambient object pairs the same
Mathlib graph with an explicit vertex \texttt{FinEnum} and adjacency decider.
The package defines an executable predicate \texttt{PowerOfTwoLength} and
proves
\[
  \mathsf{PowerOfTwoLength}(n)
  \quad\Longleftrightarrow\quad
  \exists k:\mathbb N,\ 2\le k\ \wedge\ n=2^k.
\]
Its complete graph-profile input consists of the constant unit branch-state
family, threshold $3$, and this decidable length predicate.  The common
\texttt{Graph.MinimumDegreeCycle.StaticInput} then generates the problem,
target, CT1 encoding, Mathlib-dart CT2 capability, deletion closure, and the
tight-endpoint theorem.  A K4 fixture supplies a length-four Mathlib cycle and
checks the generated CT1 C1 run.  CT2 proves that every dart in a minimal
counterexample has an endpoint of degree three.

This package is a partial implementation.  Its formal development stops after
the exact statement bridge, CT1 target search, and CT2 deletion criticality;
\texttt{Erdos64EG.OfficialStatement} remains unproved.  In particular, the
package makes no claim of a complete proof of Erd\H{o}s Problem~64.

\section{External complete instantiation: greedy coloring}
\label{app:greedy-coloring-example}

Let $G$ be the Mathlib simple graph contained in an explicitly finite
\texttt{Graph.FiniteObject}.  The package
\texttt{examples/greedy\_coloring} proves
\[
  G.\mathsf{Colorable}(\Delta(G)+1).
\]
The application-level theorem is a direct call to
\texttt{Graph.GreedyColoring.colorable\_maxDegree\_succ}; the proof algorithm
and all tactic capabilities belong to the framework.

The graph object supplies an explicit duplicate-free vertex enumeration and
an adjacency decider.  The framework derives the ordered neighbour lists,
degrees, maximum degree, and the bound
$|N^+(v)|\leq \Delta(G)$ for every suffix of the declared vertex order.  CT12
executes the canonical head-peeling machine on this order and reaches its
exhausted terminal after exactly $|V(G)|$ iterations.

The reverse fold colors an already colored suffix before its head.  At a head
$v$, CT4 receives the color type $\mathsf{Fin}(\Delta+1)$ as its demand
universe and the later-neighbour positions as its payer universe.  A payer is
eligible for precisely the color of its neighbour.  Eligibility is
functional, and
\[
  |N^+(v)|\leq\Delta<\Delta+1.
\]
The framework theorem
\texttt{FunctionalCardinalityProfile.run\_terminal\_eq\_missing} therefore
forces the exact CT4 run to the missing-payer terminal.  Its residual supplies
the first color unused by the suffix.  The profile generates the weights,
capacities, comparison data, and terminal proof within the framework.

\begin{figure}[ht]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[node distance=8mm and 10mm]
  \node[ctauthor] (object) {\textbf{Static graph input}\\
    Mathlib $G$; vertex \texttt{FinEnum}; adjacency decider};
  \node[ctderived,right=of object] (schedule) {\textbf{Framework computation}\\
    vertex order; neighbour lists; $\Delta$; bounded-order certificate};
  \node[ctcertificate,above right=5mm and 10mm of schedule] (ct12) {
    \textbf{CT12 schedule audit}\\head/tail peeling; strict decrease; exhausted terminal};
  \node[ctderived,below right=5mm and 10mm of schedule] (fold) {
    \textbf{Reverse coloring fold}\\one generated CT4 functional-cardinality run per vertex};
  \node[ctcertificate,right=of fold] (coloring) {\textbf{Mathlib coloring}\\
    $V(G)\to\mathsf{Fin}(\Delta+1)$; adjacency validity};
  \node[ctcertificate,right=of coloring] (ct1) {\textbf{CT1 validation}\\
    realization certificate; C1 terminal};

  \draw[ctinputarrow] (object) -- (schedule);
  \draw[ctderivedarrow] (schedule) -- (ct12);
  \draw[ctderivedarrow] (schedule) -- (fold);
  \draw[ctderivedarrow] (fold) -- (coloring);
  \draw[ctderivedarrow] (coloring) -- (ct1);
\end{tikzpicture}%
}
\caption{Framework-owned greedy-coloring pipeline.  The sole static input is
the explicitly finite Mathlib graph object.  CT12 audits the declared peeling
schedule, each recursive coloring step obtains its color from an exact CT4
residual, and CT1 validates the completed coloring.}
\label{fig:greedy-coloring-flow}
\end{figure}

The concrete $K_4$ fixture computes the color vector $(3,2,1,0)$ in the
declared vertex order.  It checks CT12 exhaustion in four iterations, the
four-node CT4 trace ending at the missing terminal, properness of the generated
coloring, and the final CT1 C1 trace.  These statements are kernel-checked in
the external package.

\section{External complete instantiation: Mantel's theorem}
\label{app:mantel-example}

Let $G$ be the Mathlib simple graph in an explicitly finite
\texttt{Graph.FiniteObject}, let $n=|V(G)|$, and let $m=|E(G)|$.  The package
\texttt{examples/mantel} proves
\[
  G.\mathsf{CliqueFree}(3) \quad\Longrightarrow\quad
  m\leq \left\lfloor\frac{n^2}{4}\right\rfloor.
\]
The application theorem calls
\texttt{Graph.Mantel.edgeCount\_le\_card\_sq\_div\_four\_of\_triangleFree}
directly.  Its problem-specific API consists of the finite graph object and
the triangle-freeness proof.

The framework enumerates oriented Mathlib darts and assigns to a dart
$x\mathbin{\to}y$ the integer budget
\[
  b(x,y)=n-d(x)-d(y).
\]
The degree-sum formula and Cauchy--Schwarz inequality, both applied through
Mathlib's finite-graph and finite-sum interfaces, give
\[
  \sum_{x\to y}b(x,y)=2mn-2\sum_{v\in V(G)}d(v)^2
\]
and
\[
  (2m)^2\leq n\sum_{v\in V(G)}d(v)^2.
\]
If $n^2<4m$, these identities imply that the total dart budget is negative.

The reusable \texttt{CT11.NegativeBudgetProfile} specializes the general
CT11 capability to an everywhere-admissible cell collection.  Its static
contract contains only the cell type and local-budget function; an invocation
supplies the ordered cells and proof that their total budget is negative.
CT11 then returns the first dart with $b(x,y)<0$, equivalently
\[
  n<d(x)+d(y).
\]
For a triangle-free graph, the two endpoint neighbour sets of any dart are
disjoint: a common neighbour would form a triangle.  Hence
$d(x)+d(y)\leq n$, which contradicts the localized residual.

\begin{figure}[ht]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[node distance=8mm and 10mm]
  \node[ctauthor] (object) {\textbf{Static graph input}\\
    Mathlib $G$; vertex \texttt{FinEnum}; adjacency decider};
  \node[ctauthor,below=of object] (hyp) {\textbf{Static theorem input}\\
    $G.\mathsf{CliqueFree}(3)$};
  \node[ctderived,right=of object] (identities) {\textbf{Framework computation}\\
    darts; degrees; $b(x,y)$; exact budget sum; Cauchy--Schwarz};
  \node[ctcertificate,right=of identities] (ct11) {\textbf{CT11 localization}\\
    input: $n^2<4m$; residual: $n<d(x)+d(y)$};
  \node[ctderived,right=of hyp] (disjoint) {\textbf{Graph-layer theorem}\\
    $N(x)\cap N(y)=\varnothing$; hence $d(x)+d(y)\leq n$};
  \node[ctcertificate,right=of ct11] (target) {\textbf{Mantel bound}\\
    $m\leq\lfloor n^2/4\rfloor$};

  \draw[ctinputarrow] (object) -- (identities);
  \draw[ctderivedarrow] (identities) -- (ct11);
  \draw[ctinputarrow] (object) -- (disjoint);
  \draw[ctinputarrow] (hyp) -- (disjoint);
  \draw[ctderivedarrow] (ct11) -- (target);
  \draw[ctderivedarrow] (disjoint) -- (target);
\end{tikzpicture}%
}
\caption{Framework-owned Mantel pipeline.  The external theorem supplies the
finite Mathlib graph and triangle-freeness.  The graph layer derives the
negative-budget CT11 invocation and the endpoint-degree contradiction.}
\label{fig:mantel-flow}
\end{figure}

The concrete $K_4$ fixture satisfies $n^2<4m$ and pins CT11's exact trace from
entry through localized-deficit termination; its canonical residual selects
the dart $0\mathbin{\to}1$.  This fixture tests the localization branch
independently of triangle-freeness.  A second fixture proves
$\mathsf{cycleGraph}(5)$ triangle-free, computes its five edges, and invokes
the completed Mantel theorem.

\end{document}
