% Separate repair sketch.  Do not input this file from erdos_64_proof.tex.
% Source-manuscript baseline while drafting:
% sha256 6cea87715450176e2b3e611a347c7147764730866c7174122e5be0445235c671

\section*{Repair sketch: closure-robust Part IV}
\label{repair:part-iv-closure-robust}

\paragraph{Status.}
This file is a repair sketch, not part of the proof manuscript.  It is
conditional only in the following audit sense: the typed node--[24]
window-density output has not yet been constructed by the genuine fixed
cold-skeleton/F2--F5 argument.  No theorem below is proposed for merger and no
diagram node is declared closed until that producer is proved and the complete
red-team audit returns PASS.

\subsection*{Frozen defect}

The failed load-bearing implication at nodes [48]--[54] is
\[
 \text{full target-relative curvature rank}
 \quad\Longrightarrow\quad
 \text{simultaneous realization of the Boolean response cube}
 \quad\Longrightarrow\quad
 \text{an additive entropy cost}.
\]
With quantifiers displayed, the antecedent available at node [47] says that
every admitted response-preserving quotient code is injective on the declared
curvature coordinates.  The realization conclusion needed by the entropy
count would instead say
\[
 \forall\varepsilon:\mathcal I\to\{0,1\}\;
 \exists s\in\mathcal S\;
 \forall i\in\mathcal I,
 \quad \operatorname{val}(s,i)=\varepsilon(i).
\]
The former statement does not imply the latter.  The fixed three-state Lean
example
\texttt{responsePreservingInjectivity\_does\_not\_realize\_cube}
proves the separation with two Boolean coordinates: every
response-preserving code is injective, each coordinate separately realizes
both values, and the joint all-true assignment is absent.

Therefore nodes [48]--[54] are removed from the load-bearing Part-IV route.
They may survive only as non-load-bearing conditional observations if a
separate simultaneous-realization theorem is later proved.  They cannot be
used to prove node [55], node [56], or the main theorem.

The smallest verified ancestor on this path is the same-context node [21]
multi-scale prefix together with the independently verified node [47]
quotient-rank bookkeeping.  The exact unresolved producer is node [24], not
node [47].  Its output must be proved on the identical minimal-counterexample
context and the identical selected packing.

\subsection*{Directed branch state}

Write
\[
 \mathfrak B_{47}=(\mathcal H_0,\preceq,\mathcal E,\mathcal I,
 \mathcal R,\mathcal V,\mathcal Q,\mathcal A).
\]
Its fields are frozen as follows.
\begin{description}
\item[$\mathcal H_0$.]
$G$ is a finite simple lexicographically minimal counterexample,
$\delta(G)\ge3$, and $G$ has no power-of-two cycle.
\item[$\preceq$.]
The root lexicographic order on $(|V(G)|,|E(G)|)$ and the already completed
finite schedules through node [21].  This repair adds no recursion.
\item[$\mathcal E$.]
The target-return, proper-core, proper-compression, target-defect,
proper-delocalization, and whole-support rank-drop exits already excluded on
the path to node [47].
\item[$\mathcal I$.]
The selected maximum induced-$P_{13}$ packing $\mathcal P$, its literal
remainder $R$, the exact incidence and surplus ledgers, and the node [47]
quotient-rank conclusion.  No Boolean-product realization and no entropy cost
belong to this register.
\item[$\mathcal R$.]
The full-rank continuation on the same $G$, pending the genuine node [24]
window-density theorem.
\item[$\mathcal V$.]
The finite packing count $p_{13}$, an integer ceiling $U_{13}$ once node [24]
produces it, the window surplus $\sigma_W$, remainder surplus $\sigma_R$,
positive deficiency $D^+(R)$, and the literal remainder vertex set.
\item[$\mathcal Q$.]
Before node [24] is proved, the queue contains the node-[24] structural
obligation.  After it is proved, the unique payload is the exact finite
window-budget tuple routed to node [55].
\item[$\mathcal A$.]
The compiled Lean provenance through node [47], the finite budget-transfer
lemma, this repair sketch, and its red-team audit.
\end{description}

Facts explicitly unavailable are: a simultaneous Boolean cube, a family of
target-complete global graph states, an entropy lower bound derived from rank,
and any density estimate belonging only to a sibling branch.

\subsection*{Exact node--[24] structural output}

For every universe level $u$, every packed minimal-counterexample context
\texttt{ctx}, and every
\[
 \texttt{node21}:
 \texttt{VerifiedP13MultiScaleCurvaturePrefix ctx},
\]
the missing fixed cold-skeleton/F2--F5 theorem must construct one ceiling
$U_{13}\in\mathbb N$ and proofs of
\begin{align}
 p_{13}(G)&\le U_{13}, \label{repair:eq:packing-ceiling}\\
 4\Bigl((15U_{13}+\sigma_W)\mathbin{\dotminus}\sigma_R\Bigr)
 &< n\mathbin{\dotminus}13U_{13}. \label{repair:eq:window-quarter}
\end{align}
Here $\dotminus$ is natural-number truncated subtraction.  The data and both
proofs must be computed from the same \texttt{ctx} and the packing literally
retained by \texttt{node21}.  The theorem may use only the genuine fixed
cold-skeleton/F2--F5 local argument and its certified bounded-overlap data; it
may not enumerate ambient vertices, states, supports, contexts, subgraphs, or
families of graphs.

In Lean this exact obligation is
\[
 \texttt{P13WindowDensityStructuralTheorem ctx node21}.
\]
The wrapper
\texttt{VerifiedP13WindowDensityOutput ctx node21}
contains that theorem as its only field.  Thus the production interface does
not manufacture node [24] from later rank or entropy information.

\subsection*{Closure-robust arithmetic route}

Assume only for this displayed implication that
\[
 h_{24}:\texttt{VerifiedP13WindowDensityOutput ctx node21}
\]
has been produced by the fixed cold-skeleton/F2--F5 proof.  Let $U_{13}$ be its
coverage ceiling.  The existing exact incidence ledger gives
\begin{equation}
 D^+(R)\mathbin{\dotminus}\sigma_R
 \le (15p_{13}+\sigma_W)\mathbin{\dotminus}\sigma_R
 \le (15U_{13}+\sigma_W)\mathbin{\dotminus}\sigma_R.
 \label{repair:eq:net-upper}
\end{equation}
The exact packing partition and \eqref{repair:eq:packing-ceiling} give
\begin{equation}
 n\mathbin{\dotminus}13U_{13}\le |R|.
 \label{repair:eq:remainder-floor}
\end{equation}
Multiplying \eqref{repair:eq:net-upper} by four and composing it with
\eqref{repair:eq:window-quarter} and
\eqref{repair:eq:remainder-floor} yields
\begin{equation}
 4\bigl(D^+(R)\mathbin{\dotminus}\sigma_R\bigr)<|R|.
 \label{repair:eq:strict-quarter}
\end{equation}
This is the literal finite node--[56] conclusion.  No limit, division,
curvature constant, rank magnitude, or entropy realization enters the proof.

Node [47] remains in the dependency chain as verified structural provenance.
Lean packages it as
\texttt{P13ClosureRobustNode47Prefix ctx node21 h24}; the numerical proof does
not consume its rank magnitude.  Node [55] is
\texttt{P13ClosureRobustNode55Budget ctx node21 h24}, and node [56] is
\texttt{p13ClosureRobustNode56Handoff}.  Their direct composition is
\texttt{p13ClosureRobustPartIV}.

\subsection*{Both-sides and selection audit}

No new entropy predicate is admitted.  The rejected predicate
``full rank realizes the Boolean cube'' fails the both-sides test because its
positive implication is false and its negative side was not a typed residual.
The closure-robust route instead consumes an already queued quantitative
payload.

\begin{center}
\begin{tabular}{p{0.19\textwidth}p{0.23\textwidth}p{0.23\textwidth}p{0.25\textwidth}}
Predicate/data & Positive payment & Negative residual & Decision \\
\midrule
Boolean cube from node [47] & none: implication false & omitted assignment has no required consumer here & reject \\
Genuine node-[24] structural theorem & exact window-quarter budget to node [55] & producer not yet proved & retain as open producer obligation, not a proof branch \\
Node-[55] finite inequality & strict-quarter net budget & logical negation remains inside the unresolved node-[24] theorem & consume after node [24] only \\
\end{tabular}
\end{center}

The invariant-ladder order is: minimality and target avoidance; selected
packing and node [21]; genuine node [24] window-density output; remainder and
incidence bookkeeping; node [47] provenance; node [55] finite budget; node
[56] strict-quarter handoff.  Rank-to-entropy is absent from the ladder.

\subsection*{Complete branch table for the repaired block}

\begin{center}
\begin{tabular}{p{0.13\textwidth}p{0.20\textwidth}p{0.18\textwidth}p{0.20\textwidth}p{0.20\textwidth}}
Entry & Exact condition & Output & Consumer & Status \\
\midrule
[47] & admitted rank-drop exits excluded on the same context & quotient/full-rank bookkeeping & retained provenance & compiled; no entropy consequence \\
[48]--[54] & proposed rank-to-Boolean-to-entropy route & none & none & removed from load-bearing proof \\
[24] available & $h_{24}$ supplies \eqref{repair:eq:packing-ceiling} and \eqref{repair:eq:window-quarter} & typed coverage and quarter budget & [55] & open until fixed cold-skeleton/F2--F5 producer is proved \\
[55] & typed node-[24] output on the same context & \texttt{P13ClosureRobustNode55Budget} & [56] & composition compiled \\
[56] & node-[55] budget & \eqref{repair:eq:strict-quarter} & Part V node [57] & composition compiled, but globally unavailable before [24] \\
\end{tabular}
\end{center}

The ``node [24] unavailable'' row is not a terminal leaf and not an added
hypothesis of the theorem.  It is the precise repair obligation.  Therefore
this sketch cannot receive PASS or be merged until its structural producer is
proved.  Once that producer exists, every row has a typed forward consumer and
the repaired Part-IV block has no dichotomy or cycle.

\subsection*{TeX--Lean correspondence}

\begin{center}
\begin{tabular}{p{0.31\textwidth}p{0.61\textwidth}}
TeX datum or implication & Lean declaration \\
\midrule
Exact node-[24] structural theorem & \texttt{Erdos64EG.Internal.P13WindowDensityStructuralTheorem} \\
Node-[24] verified wrapper & \texttt{Erdos64EG.Internal.VerifiedP13WindowDensityOutput} \\
$U_{13}$ and $p_{13}\le U_{13}$ & \texttt{VerifiedP13WindowDensityOutput.coverage} and \texttt{P13CoverageResidual.packing\_le} \\
Equation \eqref{repair:eq:window-quarter} & \texttt{VerifiedP13WindowDensityOutput.quarterBudget}; \texttt{P13QuarterNetBudget} \\
Equation \eqref{repair:eq:net-upper} & \texttt{p13NetDeficiencyNumerator\_le\_coverageBudget} \\
Equation \eqref{repair:eq:remainder-floor} & \texttt{VerifiedP13RemainderResidual.large} \\
Scaled transitivity & \texttt{StructuralExhaustion.Core.FiniteBudgetTransfer.strict\_scaled\_of\_le\_of\_lt\_of\_le} \\
Node [47] same-context provenance & \texttt{P13ClosureRobustNode47Prefix}; \texttt{p13ClosureRobustNode47Prefix} \\
Node [55] & \texttt{P13ClosureRobustNode55Budget}; \texttt{p13ClosureRobustNode55Budget} \\
Node [56] & \texttt{p13ClosureRobustNode56Handoff}; \texttt{p13ClosureRobustPartIV\_strictQuarter} \\
Countermodel to rank-to-cube & \texttt{StructuralExhaustion.Examples.BooleanStateEntropy.responsePreservingInjectivity\_does\_not\_realize\_cube} \\
\end{tabular}
\end{center}

The problem-specific layer supplies only the concrete packing, surplus,
deficiency, remainder, and same-context wrappers.  The scaled arithmetic is
owned by Core and exercised by
\texttt{StructuralExhaustion.Examples.FiniteBudgetTransfer}.

\subsection*{Practicality and termination}

The repaired production route enumerates no universe.  After node [24] is
supplied, it performs a constant number of natural-number additions,
multiplications by the fixed constants $4$, $13$, and $15$, truncated
subtractions, and order compositions.  It has no recursion and hence no
decreasing-measure obligation.  The missing node-[24] proof must expose a
locally checkable fixed cold-skeleton/F2--F5 certificate and bounded-overlap
ledger; this sketch does not prescribe or assume an ambient-size search.
