\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,booktabs,longtable,array}
\usepackage[margin=1in]{geometry}

\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\newcommand{\Pow}{\mathsf{Pow}_2}
\newcommand{\Exit}{\mathsf{SparseExit}}
\newcommand{\Fan}{\mathsf{TypeB}}

\title{Node [144] repair laboratory:\\
exact routing germs and the delayed $P_{13}$ consumers}
\author{Structural-exhaustion repair sketch}
\date{15 July 2026}

\begin{document}
\maketitle

\paragraph{Status.}
This is repair iteration 2 and is separate from
\texttt{proofs/erdos\_64\_eg/erdos\_64\_proof.tex}.  It freezes the exact
node-[144] residual, audits the actual coordinates of the proposed routing
label, and executes the deterministic comparison of two actual rooted germs.
It does not interpret the routing label as a CT8 external type.  The source
manuscript had SHA-256
\begin{center}
\texttt{59ca045186cd45af9b34cacad71fcb91fad2fa7b8b78628d9691f8d7ffb287eb}
\end{center}
when this laboratory was created.  No statement below is added as a
hypothesis of the main theorem.  The present verdict remains \emph{open and
blocking}: the geometric trichotomy and fixed coarse-label cap are available,
but the delayed $P_{13}$ mismatch/compatibility classifier and all three
geometric branch consumers are not derived.

\section{Defect freeze}

The stable node is [144].  Its immediate verified predecessors are the three
class audits [140], [142], and [143].  In Lean their common output is a
literal
\texttt{Core.GreedyMatchingStar.Pattern} inside the exact overloaded
token--role fibre returned at [137] and routed at [139], [141].  Thus the
smallest verified ancestor is not an assumed ``large pattern'': it is the
typed overload residual, its unique token class, and the pattern produced by
\texttt{Graph.SurplusHomogeneousPattern.audit}.

The failed implication has two logically distinct parts.  The local part is
\[
 |\mathcal M|>Q_{\rm geom}
 \quad\Longrightarrow\quad
 \Exit\ \text{or}\ \Fan .                                      \tag{D144a}
\]
The asymptotic part sets $L_{\rm geom}=Q_{\rm geom}+1$ and uses
$L_{\rm geom}$ as a graph-independent homogeneous cap:
\[
 \neg\Exit\wedge\neg\Fan
 \quad\Longrightarrow\quad
 \sigma(G)=O(\sqrt n).                                          \tag{D144b}
\]
The definition preceding (D144a) says only that the routing-label set for the
current graph is finite.  It gives neither a fixed alphabet nor a bound
independent of $G$ and $n$.  Moreover, equality of the listed routing label
is not proved to imply equality of target response in every compatible
outside context.  Both omissions are load-bearing in (D144b).

This is a level-2 structural defect.  It becomes a level-3 interface question
only after the finite-label candidate below fails the both-sides test.

\section{Frozen directed branch state}

The active state is
\[
 \mathfrak B_{144}=(H_0,\prec,\mathcal E,\mathcal I,
                    \mathcal R,\mathcal V,\mathcal Q,\mathcal A).
\]
Its fields are as follows.

\begin{longtable}{>{\raggedright\arraybackslash}p{0.15\textwidth}
                  >{\raggedright\arraybackslash}p{0.77\textwidth}}
\toprule
Field & Exact value and producer \\
\midrule
$H_0$ & The selected packed finite simple graph, minimum degree three,
target avoidance, and lexicographic minimality inherited before [125]. \\
$\prec$ & The declared vertex, surplus-slot, scheduled-pair, blocker, token,
role, and overloaded-fibre orders fixed by [127]--[141]. \\
$\mathcal E$ & The named sparse surplus exits are absent on the surviving
subbranch; decorated Type B data already produced on another local branch are
routed rather than discarded. \\
$\mathcal I$ & Full activated surplus family; exact complete-pair schedule;
canonical blocker decision; capacity token and one of 25 total roles; exact
CT9 fibre; literal window/remainder/primitive constructor; greedy matching or
star certificate. \\
$\mathcal R$ & One selected role-homogeneous same-token pattern whose edge
list is a sublist of the exact overloaded fibre. \\
$\mathcal V$ & Actual vertices, darts, selected ports, pair supports,
canonical blocker support when present, retained free-pair connector, token,
role, and pattern edges.  No routing-support, BFS-germ, or first-separator
value has yet been defined. \\
$\mathcal Q$ & A future sparse-exit payload or complete decorated Type B fan
payload, neither of which has yet been constructed. \\
$\mathcal A$ & Part-X diagram rows and the TeX--Lean--web index through
[143]. \\
\bottomrule
\end{longtable}

The near-cubic spine at [138] is an outgoing sibling of the positive-overload
branch.  It is not an input to [144].  A Type B consumer may be reused only
after all fields of its existing trigger are constructed from
$\mathfrak B_{144}$.

\section{Quantifier normalization}

For a token $t$, total role $r$, and pair $\pi$ in the exact fibre, the
manuscript proposes a routing label
\[
 \lambda_G(\pi;t,r)\in\Lambda_G.
\]
The literal statement supplied is
\[
 \forall G\quad |\Lambda_G|<\infty.                             \tag{F}
\]
The cap argument needs the stronger statement
\[
 \exists Q_0\in\mathbb N\ \forall G\quad |\Lambda_G|\le Q_0,   \tag{U}
\]
together with a post-pigeonhole theorem which compares the two actual germs
and routes every geometric outcome.  All-context response reflection is
\emph{not} required of the coarse label: equality of labels only selects two
edges.  Statement (F) nevertheless does not imply (U).

The two obligations must be kept separate.  First, each literal coordinate
of the displayed routing label needs a graph-independent range bound.  Second,
after two edges have been selected, the exact germs need a complete branch
table.  A coarse collision is legal and is supposed to be consumed by that
second table; it is not by itself a defect.

The coordinate audit leaves no range obstruction once the $P_{13}$ attachment
inventory is delayed until after the pigeonhole selection.  Endpoint
orientation, open/triangular status, germ terminal role, and the branch flags
have fixed finite ranges.  The token subtype and total role are already
constant on the incoming fibre.  The manuscript's boundary-degree coordinate
is the piece-local profile of the fixed bounded port support.  At the
degree-three baseline it may be capped to $0,1,2,{\ge}3$, so its six fixed
coordinates have at most $4^6$ values.  The fixed coarse code may simply omit
the $P_{13}$ coordinate.  After two edges collide in that code, one scans the
two selected germ supports against all selected $P_{13}$ windows and retains
the complete variable-size attachment relation.  With windows represented by
their thirteen ordered vertices, the direct nested scan has a static
$O(13n^2)$ bound.  Thus failure of a uniform all-entry code is a warning about
where the inventory is computed, not a cap obstruction.  The remaining
obligation is a leaf-total consumer for the post-selection attachment scan.

\section{A finite-context countermodel}

The obstruction already appears in two-terminal path pieces and therefore
does not depend on a complicated graph family.

\begin{definition}[Path response]
For $a\ge1$, let $X_a$ be a two-terminal path of length $a$.  For $d\ge1$,
let $K_d$ be a second internally disjoint path of length $d$ with the same
two terminals.  Gluing $X_a$ and $K_d$ produces a cycle of length $a+d$.
Put
\[
 \rho_a(d)=1
 \quad\Longleftrightarrow\quad
 \Pow(a+d),
\]
where $\Pow(m)$ means $m=2^k$ for some $k\ge2$.
\end{definition}

\begin{lemma}[Every two path lengths are context-separated]
If $1\le a<b$, then there is $d\ge1$ such that
\[
 \rho_a(d)=1,\qquad \rho_b(d)=0.
\]
\end{lemma}

\begin{proof}
Put $\delta=b-a>0$.  Choose $k\ge2$ with
\[
 2^k>a\qquad\text{and}\qquad 2^k>\delta,
\]
and set $d=2^k-a$.  Then $d\ge1$ and $a+d=2^k$, so
$\rho_a(d)=1$.  On the other hand
\[
 b+d=2^k+\delta.
\]
Since $0<\delta<2^k$, one has
\[
 2^k<2^k+\delta<2^{k+1}.
\]
There is no power of two strictly between two consecutive powers of two;
hence $\rho_b(d)=0$.
\end{proof}

\begin{corollary}[Infinite context index]
The response functions $\rho_a:\mathbb N_{>0}\to\{0,1\}$ are pairwise
distinct.  Consequently there is no finite set $\Lambda$, map
$c:\mathbb N_{>0}\to\Lambda$, and decoder
$D:\Lambda\times\mathbb N_{>0}\to\{0,1\}$ satisfying
\[
 D(c(a),d)=\rho_a(d)
 \quad\text{for every }a,d\ge1.
\]
\end{corollary}

\begin{proof}
The lemma separates every $a<b$, so an exact code $c$ must be injective.
An injective map from the positive integers to a finite set does not exist.
\end{proof}

This is only an unrestricted path-response warning.  It proves that a coarse
finite label cannot silently be promoted to an exact all-context path type.
It does \emph{not} realize the minimum-degree-three, target-avoiding,
same-token, same-role, no-exit node-[144] residual, and it does not attack the
use actually needed here, where equal labels merely select two actual germs.
Accordingly it supplies neither a counterexample to the routing lemma nor a
range counterexample for any listed label coordinate.

\section{Both-sides candidates}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.18\textwidth}
                  >{\raggedright\arraybackslash}p{0.20\textwidth}
                  >{\raggedright\arraybackslash}p{0.22\textwidth}
                  >{\raggedright\arraybackslash}p{0.15\textwidth}
                  >{\raggedright\arraybackslash}p{0.15\textwidth}}
\toprule
Predicate & Positive payment & Negative residual & Consumer & Verdict \\
\midrule
The listed routing label lies in a fixed finite code & Pigeonhole gives a
repeated code & A label component has unbounded range or multiplicity & No
current CT trigger & Reject \\
Equal routing code decides all compatible contexts & CT8 can remove or
compare the repeated state & Coarse collision (C) with a concrete outside
path context & CT3 accepts the distinguishing context only after the exact
two pieces and interface are constructed & Reject as currently stated \\
Every selected germ has length at most a fixed $K$ & Bounded pieces admit a
finite exact-type table, after CT3 equivalence is proved & A germ longer than
$K$ & CT17 additionally requires a compatible bounded offset family, which a
single long germ does not supply & Reject \\
The two germs have a first separator & A high separator is a candidate Type B
centre; a cubic separator enters the sparse switch audit & Parallel germs,
including equality and proper-prefix cases & CT7/CT3 only after a common
interface, exact pieces, and response comparison are built & Admit only as a
geometric sub-dichotomy, not as a closure \\
All exact Type B trigger fields hold at a high separator & Constructs the
existing decorated fan handoff & First failed fan-safety field, with the
literal failing tails and labels & Direct cycle, CT3 defect/compression, or
delocalization according to the failed field & Candidate invariant after
germs exist \\
\bottomrule
\end{longtable}

The earliest ladder-ready post-selection invariant is the
separator/parallel dichotomy.  It does not need an all-context external type.
Iteration 2 constructs exact canonical connectors in the selected graph and
makes this dichotomy measurable.  This geometric progress does not repair the
separate post-selection attachment-consumer obligation.

\section{CT worksheets}

\subsection*{Rejected CT8 worksheet}

\begin{description}
\item[Instance.] Node [144], proposed finite routing-label repetition.
\item[Input.] The exact predecessor pattern edge list and its token--role
fibre.
\item[S-Def.] Fails.  No fixed finite exact-type alphabet is defined; the
listed label is graph-dependent and omits unbounded target-relevant path
length.
\item[S-Dich.] Finite pigeonhole would be valid after S-Def, but cannot repair
an inexact type.
\item[S-Equiv.] Unproved and unnecessary for the intended selection use.  The
unrestricted path-response example only warns that it cannot be assumed.
\item[S-Det.] The predecessor pattern and pair order are deterministic.  The
shared BFS tie-break, selected germs, and typed geometry comparison are now
defined, but they do not turn the routing label into a CT8 exact type.
\item[S-Rout/S-Trig.] A separating context can route to CT3 only after its two
boundaried pieces are constructed.  The current predecessor output contains
no such payload.
\item[S-Comp.] The coarse selection code has the fixed bound $884736$, but the
variable delayed attachment inventory is intentionally not a CT8 alphabet.
\item[Contract correction.] The live CT8 contract has a caller-supplied finite
response family and a caller-supplied total
\texttt{remove : State -> State -> SmallerObject}.  CT8 does not construct a
target-preserving smaller representative and no CT8-to-CT10/CT3 route is
registered for this predecessor.
\item[Outcome.] Reject CT8 at this node.  The manuscript needs only ordinary
composition of coarse-label selection with exact germ comparison.
\end{description}

\subsection*{Admissible geometric worksheet seed}

\begin{description}
\item[Instance.] Node [144], canonical-germ comparison before any finite-type
claim.
\item[Input.] One exact predecessor pattern and two distinct pattern edges,
selected in the inherited order.
\item[Parameters.] Literal token root, the two literal three-vertex port
supports, and a canonical shortest connector in the already proved connected
selected object.  This is a weaker support than the manuscript's eventual
$Z(\pi;t,r)$ and is sufficient only for the finite geometric split.
\item[S-Def.] Implemented generically in
\texttt{Core/RootedPathRelation.lean} and connected to the exact token and
scheduled-pair types in
\texttt{Graph/SurplusRoutingGerm.lean}.  The graph object supplies a canonical
finite connector from the singleton token root to each nonempty port support.
\item[S-Dich.] Delete the maximal common initial edge word.  Exactly one of
parallel, first separator of degree three, or first separator of degree at
least four occurs.
\item[S-Pers.] Token, total role, selected pair endpoints, open/triangular
responses, target avoidance, and all previously absent exits remain attached
to the same packed context.
\item[S-Det.] The canonical connector and the first unequal next vertex are
functions of the supplied finite graph data.  The checker performs at most
the length of either germ many equality tests.
\item[S-Rout.] Parallel response separation constructs a CT3 target-defect
payload; a certified smaller target-complete representative constructs C2;
a cubic switch failure constructs the corresponding named sparse-exit
payload; a safe high separator constructs the full existing Type B trigger.
\item[S-Trig.] Each route must populate the existing consumer's complete
boundary, context, support, target, rank, fan-safety, and provenance fields.
\item[S-Comp.] The fixed coarse scan has bound $884736$; after selection the
complete window-attachment inventory is computable within the static
$O(13n^2)$ envelope.  No exact runtime counter is claimed.
\item[Outcome.] The geometric seed and the fixed coarse range bound compile in
their respective generic layers.  They prove no delayed-attachment consumer,
parallel reduction, switch exit, or decorated Type B handoff, and hence do not
yet prove either (D144a) or (D144b).
\end{description}

\section{Autonomous lemma-derivation ledger}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.18\textwidth}
                  >{\raggedright\arraybackslash}p{0.18\textwidth}
                  >{\raggedright\arraybackslash}p{0.18\textwidth}
                  >{\raggedright\arraybackslash}p{0.18\textwidth}
                  >{\raggedright\arraybackslash}p{0.18\textwidth}}
\toprule
Required statement & Available inputs & Attempt & Countermodel/refined
residual & Disposition \\
\midrule
Uniform fixed routing alphabet & Finite graph, finite pattern, listed label
coordinates & Omit the $P_{13}$ attachment inventory from the pre-selection
code & The remaining piece-local profile has the fixed capped range $4^6$ and
the complete window inventory can be scanned after selecting two edges & PASS
for coarse selection; the delayed scan moves the obligation to its two
post-selection leaves \\
Finite context reflection & Coarse routing-label equality & Treat the label
as CT8 exact type & Unrestricted $X_a,X_b$ are separated by $K_{2^k-a}$, but
are not realized in the node-[144] residual & Not an obligation for ordinary
coarse-label selection; do not use CT8 \\
Long germ routes to CT17 & One germ of length $>K$ & Use length as a sparse
target offset & CT17 needs several compatible realizable offsets in the same
branch state; one path supplies none & Rejected \\
Parallel germs close by compression & Two parallel paths with the same
listed label & Identify endpoint-labelled coordinates & Target-completeness
does not construct a strictly smaller admissible representative & Refine to
CT3 defect or proof-carrying C2 representative \\
High separator gives Type B & Separator and two tails & Package centre and
tails & Adjacency and deletion criticality recover two distinct indexed cubic
ports, but do not prove their open/triangular compatibility, remainder-side
membership, four assignments, fan admissibility, or marked/unmarked provenance
& Refine every failed fan field to its typed sparse exit and send only the
all-safe surplus payload to the fan-closed ledger \\
\bottomrule
\end{longtable}

No failed statement is retained as a hypothesis.  Each failure either has a
finite countermodel or becomes a typed positive residual.

\section{Leaf-totality table}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.18\textwidth}
                  >{\raggedright\arraybackslash}p{0.23\textwidth}
                  >{\raggedright\arraybackslash}p{0.18\textwidth}
                  >{\raggedright\arraybackslash}p{0.16\textwidth}
                  >{\raggedright\arraybackslash}p{0.17\textwidth}}
\toprule
Branch & Exact residual & Local object & Route & Status \\
\midrule
No repeated coarse label under the fixed code without $P_{13}$ & Injective
label scan on the selected pattern & Coordinate product certificate & Existing
homogeneous cap accounting & Available with the fixed $884736$ coarse bound \\
Repeated coarse label & Two literal pattern edges with equal listed code &
Two canonical rooted connectors plus a complete delayed scan of all selected
window attachments & Ordinary composition into the geometric trichotomy and
the attachment classifier & Geometry implemented; attachment leaves blocking \\
Parallel germs, response separated & Concrete outside context distinguishes
the two boundaried pieces & CT3 target-defect payload & Existing CT3 defect
consumer & Ready only after piece construction \\
Parallel germs, response equal & All-context equality plus a certified
strictly smaller admissible representative & Replacement certificate & C2 &
Ready only when representative is constructed \\
Cubic separator & Degree exactly three and first failed switch field & Finite
switch support & direct target, CT3 defect/compression, or delocalization &
Requires exact field classifier \\
High separator, unsafe & Least failed Type B trigger field & Two tails and
the failing local certificate & named sparse exit & Requires exact field
classifier \\
High separator, safe & Every surplus-fan trigger field & Two recovered cubic
ports plus the complete fan-closed/admissibility payload & Type B fan ledger &
Blocking: fan compatibility, remainder membership, assignments, and
marked-or-bridge provenance are absent \\
Unrestricted coarse external type & Equal coarse code, different path
response in an unattached path family & Arithmetic warning only & No node
consumer & Not a node-[144] leaf and not an obstruction verdict \\
\bottomrule
\end{longtable}

The table is not leaf-total for the source theorem.  Unbounded $P_{13}$
adjacency is no longer a uniform-code obstruction, because the complete
variable inventory is delayed until after coarse selection.  Its mismatch and
compatibility leaves still lack consumers, and the parallel, cubic, and
high-separator payload obligations remain blocking.  The
unrestricted infinite-index lemma is not a terminal leaf.

\section{Field-by-field consumer audit, iteration 2}

\subsection*{Pre-selection cap}
The exact profile currently used by the generic replacement theorem is the
piece-local boundary degree.  A reusable Lean lemma now proves that, for a
minimum-degree threshold $d$, it suffices to retain
\[
  v\longmapsto \min\{d_X(v),d\}.
\]
Indeed, below $d$ equality of capped values is exact equality, while at or
above $d$ the replacement boundary already meets the baseline before the
outside contribution is added.  At $d=3$ this gives four values per boundary
coordinate.  The proof uses the exact gluing identity
\(d_{X\oplus K}(v)=d_X(v)+d_K(v)\) and the convention that the outside owns no
boundary--boundary edge.

This is the profile intended by the manuscript notation
$\mathbf d_\partial$: it is piece-local, not the ambient degree vector.  Since
the two bounded port supports have boundary indexed by
$\mathsf{Bool}\times\mathsf{PortRole}$, there are exactly six coordinates and
their capped profile has at most $4^6$ values.  The remaining cap obligation is
therefore discharged by omitting $P_{13}$ from the fixed code.  The remaining
obligation is the delayed scan's total consumer below.

\subsection*{Public boundaried-gluing ownership API}
The reusable gluing API is independently PASS.  It exports public injective
embeddings of the piece and context vertex types into their common glued type,
identifying equal boundary labels while keeping the two internal summands
disjoint.  Its complete adjacency theorem is an if-and-only-if: every glued
edge has an actual piece or context witness through those embeddings, and
every such owned local edge is a glued edge.

Two public reconstruction helpers turn this contract into a graph isomorphism.
The first accepts a vertex equivalence and exact adjacency reflection.  The
second accepts an owned vertex partition, soundness of each local edge set,
and exhaustiveness saying that every ambient edge is owned by one of the two
sides.  Thus later switch code need not unfold the gluing implementation or
silently assume an edge partition.  The non-Erdős path fixture glues two
one-edge sides across one boundary vertex and reconstructs the resulting
three-vertex path using only the public embeddings and ownership theorem.
Public imports and the full affected build pass.

The generic \texttt{CubicStarDecomposition} specialization is now
independently PASS.  It uses universe-polymorphic labels
\texttt{ULift (Fin 3)} and one internal \texttt{ULift Unit} centre, with the
outside internal type defined as the complement of the exact four-vertex star
support.  The piece owns all centre incidences and all ambient edges between
boundary vertices; the normalized outside owns every remaining edge and no
boundary--boundary edge.  A bijective combined-vertex map, soundness of both
sides, and exhaustive edge ownership feed the public gluing helper and produce
an exact graph isomorphism back to the ambient object.

The piece satisfies internal baseline three and is preconnected.  Boundary
ownership and exclusion from the context are public theorems.  Constructing
the outside complement tests at most four fixed support vertices per declared
ambient vertex, giving the honest linear budget $4n$.  The branching fixture
executes reconstruction, baseline, preconnectedness, boundary ownership,
centre reflection, and the exact cost.  Public imports, full affected build,
and trust audit pass.

This removes the cubic-star-to-piece ownership blocker.  It still attaches no
CT3 target-response equivalence, distinguishing context, certified smaller
replacement, or delocalization witness.  Those remain semantic consumer
obligations rather than defects in the decomposition or gluing interface.

\subsection*{Fixed coarse code and delayed $P_{13}$ scan}
On a fixed token--role fibre define
\[
\begin{split}
 \mathsf{FixedCoarseCode}:={}&
 \mathsf{Bool}_{\rm orient}
 \times \mathsf{PortType}^{\mathsf{Bool}}
 \times \mathsf{PortRole}^{\mathsf{Bool}}\\
 &\times
 \bigl(\mathsf{CappedDegree}_3^{
          \mathsf{Bool}\times\mathsf{PortRole}}\bigr)
 \times \mathsf{BranchFlag}.
\end{split}
\]
Here $|\mathsf{PortType}|=2$, $|\mathsf{PortRole}|=3$,
$|\mathsf{CappedDegree}_3|=4$, and
$|\mathsf{BranchFlag}|=3$.  Total role and token subtype are fixed before the
pigeonhole step.  Therefore
\[
 |\mathsf{FixedCoarseCode}|
 \le 2\cdot2^2\cdot3^2\cdot4^6\cdot3=884736.          \tag{Q144}
\]
The code intentionally contains no selected-window attachment coordinate.
After two pattern edges with equal code are chosen, enumerate every selected
window $W$, its thirteen ordered positions, and every vertex of each selected
germ support, recording the actual adjacency relation.  Vertex-disjointness of
the windows bounds their number by the ambient order, so this literal scan has
static work $O(13n^2)$.  Its output is a finite, variable-size bipartite
attachment inventory; no uniform padding or graph-independent entry count is
needed.

The earlier hub family still proves that the literal all-appearing-entry list
has no fixed length, but it no longer obstructs (Q144).  It only forbids moving
the delayed inventory back into the fixed code.

\subsection*{Audit of the two delayed-scan leaves}
The natural first split is ``mismatch'' versus ``compatible inventory.''
Neither label is presently a consumer payload.

On the mismatch leaf, the first unequal incidence supplies only a selected
window, a position, and one side on which an adjacency differs.  It does not
by itself supply the outside vertices and connector paths, internal
disjointness, or the length identity needed for a target cycle; nor does it
name and populate an existing sparse-exit payload.  The bare implication from
mismatch to a cycle is false even locally: take one induced $P_{13}$ and attach
two new leaves at two different path vertices.  Their attachment rows differ,
but the resulting graph is a tree and has no cycle.  This is not asserted to be
the exact node-[144] host state; it rejects only the payload-free mismatch
inference.  A valid mismatch route must return the concrete connector/outside/
disjointness/length data for a target cycle or a complete named exit.

On the compatibility leaf, equality of the scanned rows produces only a
bipartite relation whose size varies with the host.  It does not construct an
all-window response theorem, a finite complete context family, a smaller
replacement, the cubic switch fields, or the fan assignments and provenance.
Pairwise or rowwise agreement is not a whole-family semantic consumer.

The token classes must remain separate during this scan.
\begin{description}
\item[Window token.] Its canonical selected-window index and position are
distinguished in the inventory, while all other incident windows are retained
rather than silently declared irrelevant.
\item[Remainder-surplus token.] It has no canonical window; the full variable
attachment inventory at the remainder root and selected germs is retained.
\item[Primitive token.] A primitive vertex, marked incidence, or selected port
also has no canonical window; again the complete scanned relation is retained.
\end{description}
A relevance projection could still simplify a class, but it is no longer
needed to prove the fixed pigeonhole cap and cannot be assumed across the
three classes.

\subsection*{Exact missing total classifier}
For each of the three token classes, a deterministic procedure must consume
the two equal coarse codes, their selected $Z^\star$ germs, the complete
delayed attachment inventories, and the typed tree-path comparison, and return
exactly one of the following proof-carrying alternatives:
\[
\begin{array}{ll}
\mathsf{A}:&\mathsf{DirectTargetCycle}
  \text{ with concrete outside/connector/disjointness/length data};\\
\mathsf{B}:&\mathsf{NamedSparseExit}
  \text{ with every field of one existing exit trigger};\\
\mathsf{C}:&\mathsf{WholeFamilyConsumer},
\end{array}                                                   \tag{O144}
\]
where alternative $\mathsf C$ is not merely ``compatible.''  It must transport
the entire variable attachment relation and, according to the typed geometric
case, return the complete parallel replacement/CT3 payload, cubic-switch
payload, root-divergence payload, or high-separator surplus-fan payload.  The
classifier must be total on mismatch and compatibility leaves and preserve the
token-class-specific root and provenance data.  No present theorem supplies
this A/B/C contract.  This post-selection classifier, rather than a uniform
$P_{13}$ code or overflow bound, is the remaining $P_{13}$ obligation.

\subsection*{Actual geometric producer}
The new compiled predecessor module
\texttt{Graph/SurplusRoutingSupport.lean} is a reusable PASS-level public
support module at its stated semantic scope.
It provides the literal root and finite support of every capacity-token
constructor, proves root membership, executes the decidable blocked/free split
with dependent evidence, and returns the canonical first-blocker support or
the already retained free connector support.  On the free branch it also
proves that both declared $\Gamma$ supports lie in that retained support.
This discharges the token-support and branch-dependent-support items of the
predecessor audit.

The module is imported by the public Graph umbrella, proves canonical-blocker
provenance and an explicit classification-work theorem, and has an independent
EvenCycle transfer example exercising root membership, both pair branches,
canonical-first fidelity, free-support inclusions, and the work bound.

It deliberately does not form one ordered union of token, port, and pair
supports; join its connected components; prove the resulting closure
connected; or run a support-restricted first-landing BFS.  It is therefore a
reusable predecessor support contract, but not yet the manuscript's
$Z(\pi;t,r)$.  In the experimental germ module, \texttt{retainedCarrier}
unions these certified token, $\Gamma$, port, and branch supports and proves
summand provenance.  That carrier is not proved connected and is not the
carrier of a restricted BFS, so its existence does not upgrade the ambient
germ or discharge the mathematical $Z$ obligations below.

The compiled prototype does not yet construct the manuscript's support
$Z(\pi;t,r)$.  It uses the already proved connectivity of the selected finite
object to choose a canonical shortest connector from the literal token root
to a literal three-vertex port support.  The six semantic token subtypes map
as follows: the two window subtypes $RW,WW$ share the selected-window-vertex
constructor and are distinguished by their existing subtype function;
remainder surplus maps to its sigma-indexed vertex; primitive $V$ maps to its
vertex; primitive $I$ to the marked end of its dart; and primitive $P$ to its
selected-port endpoint.  Thus the root map is total on the exact Lean token
sum, but the connector is only a weaker whole-object germ.

The Core comparison now retains the last common vertex, both distinct next
vertices, and their inequality.  Combining it with minimum degree three gives
the exhaustive typed output
\[
 \mathsf{parallel}\mid
 \mathsf{cubicSeparator}(z,x,y,x\ne y,d(z)=3)\mid
 \mathsf{highSeparator}(z,x,y,x\ne y,d(z)\ge4).
\]
The generic repair now builds the union of token support, both demand paths,
both port supports, and the blocker support or retained free connector, then
closes it under one shared rooted BFS tree and uses the resulting canonical
words in the classifier.  To claim equivalence with the manuscript germ, it
still has to identify this closure with the support asserted in the source and
transport the source-specific edge and exit provenance.
The support module now supplies:
\begin{enumerate}
\item a \emph{token-support} function for every one of the six semantic token
subtypes, rather than only a token root;
\item for each edge of the overloaded fibre, a dependent witness selecting
the blocked branch with its tagged canonical blocker or the free branch with
its already retained connector;
\end{enumerate}
The generic repair candidate now supplies:
\begin{enumerate}
\item one unified, duplicate-insensitive ordered support containing that token
support, both literal port supports, and the branch-dependent support;
\item a canonical closure $Z^\star$ obtained by adjoining the single shared
root-BFS path to every retained-carrier vertex, with the token root and all six
retained summands included and an internal root walk for every vertex of
$Z^\star$;
\item for each literal port support, the minimum-depth target with declared
vertex order breaking ties, together with first-landing and shortest-to-target
theorems; and
\item containment of both selected germs in $Z^\star$ and their direct input
to the shared typed tree-path classifier.
\end{enumerate}
This completes the generic geometry/carrier integration candidate.  It is not
yet identified with the manuscript source: no theorem proves that $Z^\star$
is the particular connected support $Z$ claimed there, or that its adjoined
ambient BFS vertices and edges carry the manuscript's required marked versus
unmarked and exit provenance.  The older independently selected whole-object
connector remains unusable as a substitute for that missing identification.

\subsection*{Root-star audit and viable BFS-closure contract}
Choosing one canonical shortest connector independently for every endpoint is
not enough for the manuscript's rooted-star argument.  Even if each choice is
individually deterministic, the collection has no proved common lexicographic
execution, no prefix-coherence theorem, and no prohibition on two paths
diverging and later reconverging.  The current experimental germs also have no
containment theorem in \texttt{retainedCarrier}.  Consequently their maximal
common initial words do not by themselves yield the disjoint connector tails
needed by the switch and fan consumers.

There is a second omitted case.  If two paths choose different first edges at
the token root, their separator is the root itself.  It has two outgoing
incidences but no incoming common-prefix incidence.  Thus, even when the root
is cubic, the assertion that ``incoming plus two outgoing incidences exhaust
degree three'' is unavailable.  The new root-incidence scan now classifies the
third incidence and the exact cubic/high degree split, but the third edge has
no automatic switch or token provenance.  This case therefore still cannot be
passed to the manuscript's after-edge cubic-switch proof.

A viable graph-owned replacement is the following
\emph{RootedBFSClosure} contract.
\begin{enumerate}
\item The input is one finite ordered carrier containing the token root and
both nonempty endpoint supports, together with a connectivity certificate.
Run one ordered BFS from the root, with parent ties broken by the declared
vertex/incidence order, and return its rooted parent tree.
\item For each endpoint support choose the terminal minimizing the
lexicographic pair (BFS distance, declared endpoint index).  Its germ is the
unique parent-tree path from the root to that terminal.
\item Define the executed closure $Z$ as the union of the selected parent-tree
paths (or retain the full reached tree together with this exact used
subsupport).  Prove root and endpoint containment and connectedness directly
from the tree paths.
\item Prove prefix coherence: any two selected root paths agree up to their
last common tree vertex.  After that vertex their tails are vertex-disjoint;
in particular they cannot reconverge.
\item Return an exhaustive relation with four geometric shapes:
\[
 \mathsf{parallel}
 \mid \mathsf{atRoot}(x,y)
 \mid \mathsf{afterEdgeCubic}(a,z,x,y)
 \mid \mathsf{afterEdgeHigh}(a,z,x,y).
\]
The after-edge payload contains the predecessor $a$, separator $z$, distinct
next vertices $x,y$, the three actual incidences $az,zx,zy$, and the relevant
degree proof.  The root payload is kept separate and must receive its own
third-incidence classifier and semantic consumer.  The generic incidence
classifier is now present; the semantic consumer is not.
\item Export exact provenance from every used tree vertex and edge back to the
ordered carrier summands, so a later sparse exit or Type-B handoff does not
silently leave the declared support.
\end{enumerate}

The coverage/depth/total-parent checkpoint of this contract is now
independently PASS.  The public \texttt{Graph.OrderedBFSTree} layer is imported
by both the Graph umbrella and the package root, has a non-Erdős $K_5$ transfer
example, and provides:
\begin{itemize}
\item executable ordered discovered/frontier layers with exact successor-layer
membership, monotonicity, root persistence, and order bounds;
\item the exact equivalence between discovery by level $s$ and existence of a
rooted graph walk of length at most $s$;
\item total discovery by the declared vertex count under preconnectedness,
including the one-vertex case rather than silently assuming order at least two;
\item an executable first-depth scan over $0,\ldots,|V|$, with membership,
order bound, root/nonroot facts, and minimality against every earlier level;
\item an executable optional first parent on a positive layer, and hence a
total parent for every nonroot vertex in a preconnected object, with graph
adjacency, exact one-level depth drop, and declared-order firstness;
\item a total walk defined by structural recursion on depth and the single
total parent map, with
\[
 \operatorname{length}(P_v)=\operatorname{depth}(v)
 =\operatorname{dist}(r,v),
\]
simplicity, a depth bound for every support vertex, the exact identity
$\operatorname{depth}(P_v[i])=i$, and adjacency of every successive indexed
pair;
\item proof-irrelevant transport between depth-indexed auxiliary walks, the
literal successor normalization, and the public equation
\[
 P_v=P_{\operatorname{parent}(v)}\mathbin{+}(\operatorname{parent}(v),v)
\]
for every nonroot vertex;
\item a literal \texttt{List.Prefix} theorem from the parent support into the
child support, and the index-level coherence fact that any vertex shared by
two root-walk supports occurs at its unique depth index on both walks;
\item prefix-through-index coherence: if a point lies on a root walk, its own
canonical support is exactly the inclusive \texttt{take} through that point;
the corresponding \texttt{getVert} theorem identifies the inclusive prefix at
every valid index, and a point shared by two walks forces equality of both
prefixes through its depth;
\item a generic executable \texttt{PrefixScan} and the tree-path specialization
\texttt{compareTreePaths}: the scan returns a literal common prefix and two
residual lists, proves both exact decompositions, and certifies that either one
residual is empty or both begin with distinct next vertices; the common word is
a literal prefix of each input, and the head-by-head scan has a static linear
budget;
\item exact suffix semantics and no reconvergence: an entry at suffix index
$i$ has depth $|C|+i$, every suffix member carries its exact indexed depth,
distinct next vertices force the two full divergent residual supports to be
\texttt{List.Disjoint}, and the theorem specialized to
\texttt{compareTreePaths} exports that disjointness directly;
\item actual graph adjacency at an exposed support boundary: whenever a tree
support decomposes as
$B\mathbin{+}[z,x]\mathbin{+}A$, the ambient graph contains the edge $zx$;
\item a Type-valued executable \texttt{TreePathComparison} classifier.  Its
longest common prefix is proved to begin at the root; equality is resolved
deterministically as \texttt{leftPrefix}, and the remaining prefix case is
\texttt{rightPrefix}.  A root split returns both real root adjacencies,
distinct next vertices, and disjoint residual supports.  A split after an
edge returns the last common predecessor--separator edge, both outgoing
separator adjacencies, distinct next vertices, and disjoint residual supports;
\item a generic nonempty-target selector: it minimizes BFS depth and then the
declared vertex order, its canonical path first lands in the target at its
endpoint, and it is no longer than any rooted walk ending in the target.  A
non-Erdős $C_6$ fixture exercises the depth tie and declared-order choice;
\item a static per-layer quadratic budget and a polynomial cumulative budget;
running the declared number of layers up to the object order gives the stated
cubic ambient bound.
\end{itemize}
The implementation uses the explicit finite searches and \texttt{Option.get}
with proved population.  It uses no \texttt{Nat.find}, choice operator, or
\texttt{noncomputable} definition in the BFS/depth/parent construction.

The shared-prefix theorem is the canonical anti-reconvergence core: any later
common vertex forces both walks to have had the same prefix through that
depth.  The generic prefix scan now packages an executable longest-common-prefix
comparison, exact left and right decompositions, and the empty-side or
distinct-next-vertex boundary.  Its $K_5$ transfer executes the immediate
root-divergence case, and its focused build and trust audit are independently
PASS.  The suffix/disjointness unit is now independently PASS as well: its
depth/index theorem covers every residual entry, its generic divergent-suffix
theorem proves full residual disjointness and hence no reconvergence, its
comparison-specific theorem applies that result to the executed scan, and its
support-boundary theorem returns the actual ambient adjacency.  The $K_5$
transfer executes both residual disjointness and boundary adjacency, with
focused build and trust checks passing.  The final typed geometry classifier
is now independently PASS.  It proves that the executed common prefix is
root-headed and deterministically returns left-prefix, right-prefix,
root-divergence, or after-edge divergence.  The root payload contains both
actual root adjacencies and disjoint residuals; the after-edge payload contains
the last common edge, all three actual adjacencies, distinct next vertices,
and disjoint residuals.  The $K_5$ fixture executes the deterministic equality
and root-divergence cases, while a separate branching-tree fixture executes
the after-edge case; focused builds and trust checks pass.  The geometry
classifier is therefore no longer open.  The generic target selector and the
\texttt{SurplusRoutingGerm} $Z^\star$ candidate are now independently PASS as
well.  The endpoint is selected by minimum BFS depth and declared order; its
tree path first lands in the literal port support and is shortest among all
rooted paths to that target.  The retained carrier is the union of token
support, two demand path supports, two literal port supports, and the dependent
branch support.  Closing this six-summand union under the one shared root-BFS
tree gives $Z^\star$, contains the token root, gives every closure vertex an
internal root walk, contains both selected endpoint germs, and feeds those
same germs to the typed classifier.  The $C_6$ target-selection transfer and
the focused builds and trust checks pass.  The associated work theorem is a
static polynomial envelope, not an exact instrumented runtime count.

Thus the generic geometry/carrier integration candidate is complete.  What
remains is identification with the manuscript source: the current theorems do
not prove $Z^\star=Z$ (or the precise weaker equivalence actually needed), nor
do they transport the manuscript's marked/unmarked and sparse-exit provenance
onto every adjoined BFS vertex and edge.

Focused builds and trust audits of the BFS layer, the $C_6$ transfer, and the
$Z^\star$ candidate pass.

The compiled work certificate is a static polynomial envelope for the shared
BFS, carrier path closure, and two endpoint selections.  It is deliberately
not presented as an exact runtime measurement.  The construction enumerates
no path family or outside-context family.

This contract repairs only the geometry and execution provenance.  The
root-divergence consumer, the delayed $P_{13}$ A/B/C classifier, and the
parallel/cubic/high field-by-field consumers remain blocking.  In particular,
non-reconverging tree tails do not manufacture target-defect contexts,
certified smaller representatives, fan assignments, or the complete
post-selection consumer (O144).

\subsection*{Root-divergence incidence audit}
The geometry-only \texttt{Graph.RootIncidence} unit is independently PASS.
From two distinct actual neighbours $x,y$ of a root $r$ and the baseline
$d(r)\ge3$, it scans the declared neighbour order and returns the first
neighbour $w\notin\{x,y\}$.  Its proof-carrying output retains $rw\in E(G)$,
$w\ne x,y$, and the exact exhaustive split
\[
 \mathsf{cubic}(d(r)=3,w)
 \quad\mid\quad
 \mathsf{high}(d(r)\ge4,w).
\]
The scan budget is the declared neighbour-list length and is at most the
ambient vertex order.  The $K_5$ transfer executes the high branch, and its
focused build and trust audit pass.  The surplus wrapper independently proves
the degree-three baseline at the actual token root and specializes the generic
classifier and budget to that root.

The adapter from the actual \texttt{divergeAtRoot} constructor returned by
\texttt{classifySelectedGerms} is now independently PASS.  The executable
\texttt{classifySelectedRootIncidence?} returns the complete classified root
divergence only in that geometric case and returns \texttt{none} for the other
three tree-path outcomes.  Its exact tag theorem proves
\[
 \texttt{classifySelectedRootIncidence?.isSome}
 =\texttt{selectedGermsDivergeAtRoot},
\]
so it neither fabricates a root split nor drops an actual one.  The payload
retains the two adjacencies and inequality already carried by the selected
tree paths and immediately runs the token-root incidence classifier.  Focused
build and trust re-review pass.  This is an ownership bridge, not a semantic
consumer.

Neither root-incidence branch closes node [144].  In the cubic branch the
three neighbours form only a rooted claw.  The four-vertex tree with centre
$r$ and leaves $x,y,w$ realizes the entire geometric payload and contains no
cycle, switch piece, or target witness.  In the actual proof, the third edge
$rw$ now belongs to the complete generic cubic-star incidence boundary, but
still lacks the node-specific piece specialization, token origin,
marked/unmarked status, and completion-edge provenance needed by a named
sparse-exit trigger.  In the high branch, the generic layers now recover typed
ports and decide open/triangular and fan compatibility, but they do not consume
a compatibility failure or produce remainder-side membership, shoulder
assignments, admissibility, or the marked Type-B handoff.

The token subtypes sharpen but do not remove this semantic gap:
\begin{description}
\item[Window tokens.] The root has a canonical window position, but the third
incidence is not thereby identified as a legal window switch or fan edge.
\item[Remainder-surplus tokens.] Positive remainder surplus forces the token
root into the high-degree branch.  Typed port recovery and local fan
classification then apply, but the failure exits and remaining Type-B fields
are still absent.
\item[Primitive vertex/incidence tokens.] The literal primitive support gives
root provenance only; it does not orient the third incidence into a consumer.
\item[Primitive-port tokens.] The declared port geometry is cubic and star
shaped, but a completion edge may already be one of the two divergent outgoing
edges.  The newly selected third edge therefore cannot be assumed to be the
completion edge or to carry its provenance.
\end{description}
Thus \texttt{RootIncidence} clears the missing-third-neighbour computation and
degree split, while the root-divergence semantic branch remains FAIL.

\subsection*{After-edge incidence audit}
The generic after-edge incidence unit and its selected-germ adapter are now
independently PASS.  The payload at a separator $z$ retains a predecessor $a$
and residual next vertices $x,y$ with all three adjacencies oriented from the
separator,
\[
 za,zx,zy\in E(G),
 \qquad a\ne x,\quad a\ne y,\quad x\ne y.
\]
The two predecessor inequalities are derived from simplicity of the canonical
tree walks, their exact common-prefix/residual decompositions, and the
resulting noduplicated-list disjointness; $x\ne y$ is retained from the
divergence classifier.  The proof is parametric in the common stem and does
not assume it is nonempty, so the immediate-after-root-edge case is covered
without a hidden prefix hypothesis.

Given the degree-three baseline, \texttt{classifyAfterEdge} returns the exact
split $d(z)=3$ or $d(z)\ge4$ and performs one degree comparison.  The branching
tree fixture executes the cubic case with all three incidences, while focused
build and trust checks cover the generic unit, including empty-stem
parametric correctness.

The ownership adapter
\texttt{classifySelectedAfterEdgeIncidence?} consumes the actual
\texttt{divergeAfterEdge} constructor returned by the two selected germs,
reorients the common-edge adjacency to $za$, derives the two missing
inequalities, and runs the exact degree split.  It returns \texttt{none} on
all other tree-path shapes.  Its tag theorem proves
\[
 \texttt{classifySelectedAfterEdgeIncidence?.isSome}
 =\texttt{selectedGermsDivergeAfterEdge},
\]
so the Option payload is present exactly on the executed after-edge branch.

This completes after-edge incidence geometry only.  The cubic result does not
construct the switch piece, boundary ownership, target-defect context,
certified compression, or delocalization witness.  The high result does not
construct indexed cubic ports, fan compatibility, remainder membership,
shoulder assignments, admissibility, or marked Type-B provenance.  Therefore
the cubic-switch and high-separator semantic branches remain FAIL.

\subsection*{Parallel consumer fields}
\begin{longtable}{p{0.25\textwidth}p{0.30\textwidth}p{0.34\textwidth}}
\toprule
Required field & Current producer & Status \\
\midrule
Common finite interface and two literal pieces & public gluing embeddings,
owned-partition reconstruction, and exact \texttt{CubicStarDecomposition} &
PASS for one cubic star; comparison of two pieces on one semantic interface
still needs the CT3 response setup \\
Concrete compatible distinguishing context & none & absent; CT3 can consume
one only after construction \\
All-context target equality & none & the cited context-universality statement
quantifies over every outside context; no finite complete generator is proved
\\
Strictly smaller admissible replacement & none & absent; equality or prefix
of path words does not construct a \texttt{SmallerObject} \\
Baseline preservation & capped piece-local theorem plus public exact gluing
adjacency/ownership API and cubic-star decomposition & available for the
decomposed cubic piece; replacement-side target semantics remain absent \\
Proper/global delocalization witness & none & absent: a larger connected
support and its first localization failure must be returned \\
\bottomrule
\end{longtable}
Thus ``parallel'' is not itself a finite consumer trigger.  A legal finite
classifier would need to return one of the concrete context, certified
replacement, or localization witnesses.  No such total classifier follows
from the two words alone.

\subsection*{Cubic-separator consumer fields}
The generic \texttt{CubicStar} producer is independently PASS.  It consumes
either a cubic after-edge incidence or a cubic root-incidence branch and
returns one centre and its three pairwise-distinct actual neighbours.  Its
support is exactly the four vertices consisting of the centre and those three
leaves; the boundary has cardinality three, the centre lies outside it, and
the full ambient neighbour finset is proved equal to that boundary.  Every
support vertex has an internal walk to the centre, hence the four-vertex
support is connected.

The exported switch ownership shape labels the three boundary vertices by
\texttt{Fin 3}, proves injectivity, makes the centre the sole internal vertex,
retains all three boundary adjacencies, and proves that every incidence at the
centre is owned by exactly this boundary image.  Its support agrees literally
with the four-vertex star.  Constructing the shape from certified incidences
costs zero primitive scans; materializing the full ambient neighbour finset is
honestly charged one adjacency decision per ambient vertex, while the support
and its cardinality are explicit.  The branching-tree transfer executes the
cubic after-edge construction, exact support and neighbour equality,
cardinality four, connected ownership shape, and both cost statements.  Public
imports, focused checks, and trust review pass.

This producer resolves the finite switch \emph{geometry}, not the switch
semantics.  The independently PASS \texttt{CubicStarDecomposition} now turns
the star into a universe-polymorphic \texttt{ULift (Fin 3)} boundaried piece
with one internal centre, the exact outside complement, a complete owned-edge
partition and ambient reconstruction, internal baseline, preconnectedness,
and linear $4n$ construction budget.  It still does not construct a
target-distinguishing CT3 context, prove a
target-complete proper-support compression with a certified smaller object, or
return a proper/global delocalization witness.  It also supplies no response
equivalence for the boundaried star.  Thus the manuscript's three semantic
possibilities remain without an executable total consumer despite complete
cubic incidence ownership.

\subsection*{High-separator consumer fields}
The generic \texttt{HighSeparatorPort} producer and its surplus wrapper are
independently PASS.  For every already certified adjacency at a high centre,
the public \texttt{HighCenterPort.neighborEquiv} recovers the typed port index;
endpoint reflection proves that applying the port endpoint map returns the
original neighbour.  Distinct neighbours recover distinct ports.

On a root-high branch the output retains typed ports for both divergent next
vertices and the selected third neighbour, proves all three endpoint
identities and pairwise inequalities, and carries the complete root source as
opaque provenance.  On an after-edge-high branch it does the same for the
predecessor and two residual next vertices.  The root and after-edge Option
constructors are populated exactly on their respective high tags, with exact
\texttt{isSome} equalities; cubic inputs return \texttt{none}.  Port recovery
uses the certified neighbour equivalence and performs zero primitive scans.
The \texttt{SurplusHighSeparatorPort} layer applies these producers directly
to the classified surplus root and after-edge sources without erasing their
provenance.  The $K_5$ transfer executes both high shapes, endpoint reflection,
pairwise port inequality, exact high tags, and the zero-cost statement.
Public imports, focused checks, the full affected build, and trust audit pass.

The next local classification layer is independently PASS as well.
\texttt{PortClass} returns the exact open or triangular equation for one typed
port.  The ordered pair classifier retains all four cases
open--open, open--triangular, triangular--open, and
triangular--triangular.  The fan classifier tests the literal compatibility
fields in order.  Its three \texttt{FanFailure} constructors retain the first
failed field together with every clean-prefix proof: first endpoint in the
second shoulder list; otherwise second endpoint in the first shoulder list;
otherwise non-disjoint shoulder lists.  \texttt{FanDecision.Valid} proves the
successful branch is exactly \texttt{FanCompatible} and every failure branch
implies its negation.

Root-high and after-edge-high tables classify the divergent pair, classify the
third or predecessor port separately, preserve the typed indices and complete
surplus source provenance, and use the actual deletion-criticality theorem.
The fixed predicate envelope charges two chord-adjacency tests, four
endpoint--shoulder equalities, and four shoulder-pair equalities, for
\texttt{PredicateBudget.total}=10.  This is a worst-case local predicate
currency, not an exact short-circuit trace.

The non-Erdős $K_{3,4}$ fixture is genuinely nontrivial: both selected ports
are classified open, both endpoint-exclusion fields pass, and the final
shoulder-disjointness field fails because the two shoulder lists coincide.
The theorem \texttt{fan\_exact} pins the executed result to that precise final
\texttt{shouldersNotDisjoint} residual, and the public theorem derives
$\neg\mathsf{FanCompatible}$.  The validity theorem, budget ten, surplus
provenance/indexing wrappers, public imports, full affected build, and trust
audit pass.

The high-port exit and route layer is independently PASS at the following
exact scope.  A shared shoulder of two distinct ports produces a literal
four-cycle unconditionally.  Either ordered endpoint-in-opposite-shoulders
failure also produces a literal four-cycle whenever either of the two ports is
triangular; the symmetric lemmas transport the witnessed endpoint edge to the
triangle on the available side.  Consequently every final shoulder-overlap
failure closes directly, and every endpoint failure in an open--triangular,
triangular--open, or triangular--triangular pair closes directly.  The
$K_{3,4}$ transfer now consumes its exact open--open final-overlap residual and
constructs the square, rather than stopping at
$\neg\mathsf{FanCompatible}$.

\texttt{PairRoute} retains all four ordered type cases
\texttt{OO}/\texttt{OT}/\texttt{TO}/\texttt{TT}, and root/after-edge route
wrappers retain the complete classified source provenance and typed port
indices.  For any classifier-selected triangular port,
\texttt{shoulderStage?} supplies the existing CT5 triangular-shoulder verified
stage from the identical high-centre setup.  Given, explicitly, a deleted-root
\texttt{DartReturn} for each extracted triangular port and target-cycle
avoidance, \texttt{returnStage?} supplies the existing CT1 verified return
stage.  Given two distinct ports in the TT case,
\texttt{crossStage?} supplies the existing CT9 cross-shoulder verified stage;
OO and mixed pairs deliberately return \texttt{none} from this TT-only
adapter.  These adapters preserve the exact port equalities, setup, and caller
provenance; they do not synthesize their CT1 return or avoidance prerequisites.
Public imports, full affected build, transfers, and trust audit pass.

The correct semantic target remains a surplus fan handoff, not the
negative-support handoff.  The compatibility classifier now either proves
\texttt{FanCompatible} or returns the ordered first failed field, but no
generic named sparse-exit payload is yet attached to every remaining failure.
The open--open branch remains live when it is compatible or when its first
failure is an endpoint--shoulder incidence: neither port supplies the triangle
needed by the square lemma.  Even on a compatible branch, typed high-centre
ports and provenance
transport do not establish the following fields required by the existing
fan-closed positive-deficit route:
\begin{enumerate}
\item membership of both cubic endpoints on the declared remainder side;
\item assignment of all four non-centre shoulder incidences;
\item an admissible fan-window profile, direct-cycle safety, target-defect,
compression, and delocalization decisions;
\item certificate-marked provenance for the local positive-deficit wrapper,
or an explicit unmarked bridge-residual payload.
\end{enumerate}
The recovered typed ports, classified pair, transported incidence provenance,
and two separated tails supply none of these four fields automatically.  Every failed item must
return its named sparse-exit certificate; the square theorems now consume all
shared-shoulder failures and every endpoint failure with a triangular side,
but not an open--open endpoint failure.  On the all-safe branch these fields form a
distinct graph-owned surplus handoff which may compose with
\texttt{FanClosedPort}; it must not be coerced into
\texttt{NegativeSupportHandoff.DecoratedHandoff}.

The present consumer audit is therefore exact but not leaf-total.  Its
blocking point is constructive: the source proof invokes global
context-universality and decorated-fan admissibility without finite producers
for their witnesses on this residual.  This is not yet called a methodology
obstruction because a finer boundaried switch/fan profile may still be
constructible from the exact support $Z$.

\section{Practicality and ownership}

The predecessor pattern is an actual finite list.  The implemented weaker
germ uses one deterministic canonical connector per selected endpoint and a
linear common-prefix comparison.  A final manuscript germ must scan only the
union of its retained supports.  If $s$ is the
number of support vertices and $e_s$ the number of support incidences, two
BFS runs and one prefix comparison cost $O(s+e_s)$.  A pair scan over a
pattern of length $m$ costs $O(m^2+m(s+e_s))$.  No path family, outside
context family, quotient family, subgraph family, or graph family is
enumerated.

The infinite-index lemma is generic arithmetic and only a warning.  The
reusable compiled units are the deterministic rooted-word comparison, the
capped piece-local gluing theorem, and the public PASS-level predecessor
support/provenance/work module with its EvenCycle transfer.  The
public OrderedBFSTree coverage/depth/total-parent/root-walk checkpoint and its
$K_5$ transfer are also PASS through exact length, distance, simplicity,
support-depth, indexed-vertex semantics, parent-concat normalization, literal
parent-prefix, shared-vertex depth-index coherence, and equality of canonical
inclusive prefixes through every shared indexed vertex.  The generic
\texttt{PrefixScan}/\texttt{compareTreePaths} checkpoint is likewise PASS for
executable longest-common-prefix comparison, exact decompositions, the
empty-or-distinct-next boundary, literal-prefix proofs, a static linear budget,
and the $K_5$ root-divergence execution.  The suffix unit is independently PASS
for exact suffix depth/index semantics, full divergent-residual disjointness,
no reconvergence, actual support-boundary adjacency, the comparison-specific
export, and its $K_5$/build/trust checks.  The typed graph-separator classifier
is independently PASS as a Type-valued executable classifier: its common
prefix is root-headed; its left/right prefix cases are deterministic; its
root-divergence payload contains real adjacencies and disjoint residuals; and
its after-edge payload contains the last common edge, all three real
adjacencies, distinct branches, and disjoint residuals.  The $K_5$ and
branching-tree fixtures execute the relevant cases, and focused build/trust
checks pass.  Geometry classification is no longer open.  The generic target
selector and \texttt{SurplusRoutingGerm} $Z^\star$ candidate are independently
PASS for minimum-depth/declared-order endpoint selection, first landing,
shortest-to-target paths, the six-summand retained carrier and token root,
root-walk connectedness internal to $Z^\star$, selected-germ containment, use
of the shared typed classifier, a static polynomial (not exact runtime) budget,
and the $C_6$ transfer/build/trust checks.  This completes the generic
geometry/carrier integration candidate, but no theorem yet identifies it with
the manuscript source support or transports all of that source's provenance.
The generic \texttt{RootIncidence} unit is also independently PASS for the
declared-order first third neighbour, exact cubic/high split, linear
neighbour-list budget bounded by ambient order, and $K_5$/build/trust checks;
the surplus wrapper supplies the actual token-root degree-three baseline.  An
adapter from the executed \texttt{divergeAtRoot} payload to this wrapper is
independently PASS: \texttt{classifySelectedRootIncidence?} returns a payload
exactly when its executable root-divergence tag is true, by the proved
\texttt{isSome} equality.  This remains geometry only: the cubic claw
countermodel and the missing switch/Type-B provenance block semantic closure.
The after-edge incidence unit and adapter are likewise independently PASS:
noduplicated tree-path decompositions give pairwise distinct predecessor and
next vertices, the payload retains all three separator-oriented adjacencies,
the exact cubic/high split costs one comparison, and
\texttt{classifySelectedAfterEdgeIncidence?} is present exactly when the
executed after-edge tag is true.  The branching fixture, focused builds, trust
audit, and the parametric empty-stem case pass.  This is also geometry only;
neither switch nor Type-B semantics follow.
The \texttt{CubicStar} producer is independently PASS for its exact
four-vertex support, boundary/full-neighbour equality, internal connectedness,
\texttt{Fin 3} switch boundary and complete centre-incidence ownership,
support/cardinality facts, zero construction scans, ambient-order neighbour
materialization cost, and branching transfer.  The
\texttt{HighSeparatorPort} and \texttt{SurplusHighSeparatorPort} producers are
independently PASS for neighbour-equivalence port recovery on root and
after-edge high branches, endpoint reflection, pairwise port inequality,
opaque source provenance, exact high Option tags, zero scan cost, $K_5$
transfer, public imports, full affected build, and trust audit.  These are
structural producers only: CT3 target/compression/delocalization and fan
semantics remain absent.  The public boundaried-gluing API is independently
PASS for its piece/context embeddings, complete adjacency equivalence,
equivalence-based and owned-partition isomorphism helpers, path reconstruction
fixture, public imports, and full build.  The
\texttt{CubicStarDecomposition} specialization is independently PASS for its
universe-polymorphic \texttt{ULift (Fin 3)}/\texttt{ULift Unit} types, exact
outside complement and edge ownership, ambient reconstruction, internal
baseline, preconnectedness, linear $4n$ budget, branching fixture, full build,
and trust audit.  Only its CT3 semantics remain missing.  The high-port
classification layer is independently PASS for exact
\texttt{PortClass}, all four ordered type pairs, first-failure fan residuals
with clean-prefix fields, \texttt{FanDecision.Valid}, surplus
provenance/indexing tables, fixed predicate budget ten, and the $K_{3,4}$
open--open final shoulder-overlap execution pinned by \texttt{fan\_exact} and
$\neg\mathsf{FanCompatible}$.  Public imports, full build, and trust audit
pass.  The independently PASS high route layer turns shared-shoulder failure
unconditionally into a square, turns either endpoint failure into a square
when at least one port is triangular, preserves the exact OO/OT/TO/TT split,
and provides triangular CT5/CT1 and TT CT9 adapters with explicit setup,
return, avoidance, distinctness, and provenance prerequisites.  The $K_{3,4}$
overlap now executes the square exit.  Open--open beyond that overlap exit and
the complete Type-B payload remain open.
No node-[144] total CT route is registered because no branch consumer is yet
total, although the reusable triangular CT adapters now execute at their exact
prerequisites.  The
next valid unit is the delayed $P_{13}$ A/B/C classifier (O144), separately for
window, remainder-surplus, and primitive token classes, followed by CT3
response semantics, the remaining open--open consumer, and the complete Type-B
fields.

\section{Repair verdict}

\section{Iteration 4: exact semantic residual interfaces}

This iteration freezes the current coarse-collision and germ geometry without
using the concurrently developed implementation module.  The purpose is to
test the lowest possible local producer--consumer interfaces.  In every row
below, the ambient graph, activation stage, overloaded token--role fibre,
homogeneous pattern, selected collision pair, token, and blocker/free branch
are retained definitionally from nodes~[140], [142], or~[143].

\begin{longtable}{>{\raggedright\arraybackslash}p{0.16\textwidth}
                  >{\raggedright\arraybackslash}p{0.25\textwidth}
                  >{\raggedright\arraybackslash}p{0.27\textwidth}
                  >{\raggedright\arraybackslash}p{0.22\textwidth}}
\toprule
Residual & Locally produced fields & Exact consumer trigger & First missing field \\
\midrule
$P_{\rm att}$ & One selected window-position--vertex coordinate, the two
rooted supports, and the proof that the two literal attachment bits differ &
A literal target cycle with its edge list, simplicity and dyadic-length
certificate, or one complete named sparse-exit witness & No connector joining
the unequal incidences, hence no cycle edge list or exit certificate \\
$P_{\rm par}$ & Two actual rooted germs, the proof that one is a prefix of the
other, equal coarse code, and equality of the delayed attachment rows & CT3
pieces on one declared boundary together with either one concrete
distinguishing context or a certified target-complete smaller representative
& No common boundaried-piece construction and no response or reduction
certificate \\
$P_{\rm cub}$ & The classified root/after-edge cubic incidence, exact cubic
star, owned $\operatorname{Fin}3$ boundary, ambient reconstruction, and equal
attachment rows & A CT3 target-defect, target-complete compression, or
delocalization certificate on that exact decomposition & The decomposition
has no target-response coordinate or context-reflection certificate \\
$P_{\rm oo}$ & A high separator, two distinct recovered open ports, their
endpoint/shoulder data, the exact compatibility-table result, and original
source provenance & A complete Type~B entry: counted remainder support,
assigned carriers, centre marking, fan assignment, safety/admissibility, and
the ledger provenance required by the existing Type~B consumer & Remainder
membership, assigned carriers, fan marking and whole-entry safety are not
consequences of two open ports \\
\bottomrule
\end{longtable}

The open--open endpoint-failure subcase is kept distinct from compatible
open--open.  The square construction available when one port is triangular
does not apply to two open ports.  Thus endpoint failure is not silently
folded into $P_{\rm oo}$'s positive compatibility side.

These four records are finite and locally measurable, but merely declaring
them as Lean structures would not repair the proof: the missing columns are
exactly the hypotheses of their proposed consumers.  A framework contract of
the form ``supply a function from each residual to a completed exit'' would
move the theorem into caller data and is therefore rejected.  CT10 can
classify the four rows, but it cannot manufacture the CT3 or Type~B
certificates.  The registered CT9--CT7 route is also inapplicable because its
source is a capacity-one overload pair, not the present classwise overload
followed by homogeneous-pattern extraction.

\subsection*{Both-sides and scope verdict}

The split is measurable: collision selection costs $O(m^2)$ for a pattern of
length $m$; two retained-support BFS and prefix scans cost $O(s+e_s)$; the
cubic and high-port tables are linear in the local neighbour list and
otherwise constant size.  No outside-context, quotient, path, subgraph, or
graph universe is enumerated.

The negative sides nevertheless have no admitted consumer trigger.  This is
not a methodology-level language obstruction.  Each missing object has an
existing finite proof language: a concrete boundaried context, a certified
smaller replacement, a CT3 response defect, or a finite Type~B assigned
support.  What is absent is a theorem constructing one of those objects from
the frozen node-[144] residual.  The defect therefore remains a level-3
pattern/producer gap, not a level-4 scope obstruction.  The first exact failed
obligation is S-Trig for $P_{\rm att}$: unequal attachment bits do not imply a
target cycle or a named sparse exit.  The pendant-leaf tree example already
records the smallest countermodel to that implication.

Consequently no new generic route or transfer example is introduced in this
iteration.  There is no successful residual-to-trigger transformation to
transfer; a prototype route would necessarily accept one of the missing
semantic certificates as caller input.  Node~[144] remains open.

The earlier methodology-obstruction verdict is withdrawn.  The unrestricted
path lemma does not inhabit the exact residual, and the routing label need not
be an external type.  Ordinary composition with an exact finite germ relation
is the right design.

Iteration 2 proves three useful but insufficient facts: deterministic
geometric trichotomy on the exact predecessor's selected object, a linear
checker, and preservation of the degree-three baseline under equality of
capped piece-local boundary degrees.  The corrected product worksheet now
omits $P_{13}$ and gives the unconditional fixed coarse bound $884736$.
Scanning the complete selected-window attachment relation only after choosing
two equal-code edges is finite with a static $O(13n^2)$ envelope, so the false
fixed entry-count claim is no longer a uniform-code obstruction.  The delayed
scan is nevertheless not leaf-total.  A mismatch alone supplies neither the
connector/outside/disjointness/length data for a target cycle nor a named exit;
an induced $P_{13}$ with two pendant leaves at different positions is the
finite tree countermodel to the payload-free cycle inference.  Compatibility
supplies only a variable bipartite inventory, not a whole-family semantic
consumer.  Window, remainder-surplus, and primitive token classes must be
handled separately.  Contract (O144) now states the exact missing total A/B/C
classifier: complete direct-target data, a complete named sparse exit, or a
whole-family payload that consumes the typed geometric branch.  Independently
chosen canonical germs also lack containment,
prefix-coherence, and non-reconvergence; RootedBFSClosure states the corrected
single-tree contract, and the public ordered-BFS classifier now implements its
complete prefix/root-divergence/after-edge geometry.  The generic target
selector and $Z^\star$ candidate now also supply endpoint selection, a
six-summand BFS-path closure, internal root connectedness, selected-germ
containment, and the same typed classifier under a static polynomial envelope.
They are not yet identified with the manuscript's source support and do not
transport its full marked/unmarked and exit provenance.  They also do not
supply the root-divergence consumer.  The independently PASS
\texttt{RootIncidence} scan now computes its first third neighbour and exact
cubic/high split within the order budget, with a surplus-baseline wrapper and
$K_5$ transfer.  The actual \texttt{divergeAtRoot} adapter is an integration
step now independently PASS, including the exact executable \texttt{isSome}
tag theorem; it is still only an ownership bridge.  A cubic claw has the
complete incidence geometry but no switch or cycle.  The high branch now has
typed ports and an exact local compatibility classification, but still lacks
failure consumers and the remaining Type-B fields.  In particular,
remainder-surplus roots land in the high branch without a Type-B payload, and
the cubic primitive-port star does not prove that the third edge has completion
provenance because a completion edge may be one of the divergent outgoing
edges.  The iteration
therefore
does not prove equivalence with the manuscript support $Z$ or any complete
parallel/cubic/high consumer.  The after-edge incidence unit and exact Option/
tag adapter now independently supply pairwise-distinct $a,x,y$, all three
oriented separator adjacencies, and the one-check cubic/high split, including
the empty-stem case.  The independently PASS \texttt{CubicStar} producer then
packages the complete cubic neighbourhood as an exact connected four-vertex
support with a \texttt{Fin 3} switch boundary owning every centre incidence,
at zero construction cost and honest ambient-order neighbour materialization
cost.  It does not construct a CT3 target context, certified compression, or
delocalization witness.  The independently PASS public gluing API and
\texttt{CubicStarDecomposition} now supply the universe-polymorphic boundary,
outside complement, complete owned partition, ambient isomorphism, baseline,
preconnectedness, and linear $4n$ construction bound.  CT3 response semantics
alone remain absent from this structural chain.  On the high branch, the independently PASS generic
and surplus port producers recover pairwise-distinct typed ports by the public
neighbour equivalence, reflect their endpoints, retain exact source
provenance, and detect exactly the high tags at zero scan cost.  The
independently PASS classification layer then decides exact open/triangular
types and all four ordered pairs, and returns either
\texttt{FanCompatible} or the ordered first failed compatibility field under
the fixed budget ten; the $K_{3,4}$ fixture pins the final shoulder-overlap
failure.  The independently PASS exit and route layer consumes every
shared-shoulder failure as a square, consumes endpoint failure whenever either
port is triangular, retains all four ordered pair routes, and exposes CT5/CT1
for each triangular port and CT9 for TT under explicit prerequisites and exact
provenance.  The open--open compatible/endpoint-failure branch is still live,
and no route constructs remainder membership, shoulder assignments,
admissibility, or marked Type-B provenance.  Thus the second red-team
disposition is still \textbf{FAIL/blocking}, but neither ambient boundary
degree nor port recovery is a blocker.  The original manuscript and node
status remain unchanged.

\end{document}
